### 2024-06-11 main.tex
Initial Overleaf Import

%% hf: enable header and footer.
\documentclass[
twocolumn,
% hf,
]{ceurart}

%%
%% One can fix some overfills
\sloppy

\begin{document}

%%
%% Rights management information.
%% CC-BY is the default license.
\copyrightyear{2024}
\copyrightclause{Copyright for this paper by its authors.
  Use permitted under Creative Commons License Attribution 4.0
  International (CC BY 4.0).}

%%
%% This command is for the conference information
\conference{BPM 2024: Demos and Resources,
  September 01--06, 2024, Krakow, PL}

\title{Instantaneous, Comprehensible, and Fixable Soundness Checking of Realistic BPMN Models}

\author[1]{Tim Kräuter}[
email=tkra@hvl.no
]
\address[1]{Western Norway University of Applied Sciences, Bergen, Norway}

\begin{abstract}
  TBD
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
BPM,
Verification,
Soundness,
Safeness
\end{keywords}

\maketitle

% Details can be found here: https://bpm2024.agh.edu.pl/call-for-demos-and-resources/

\section{Introduction}
\cite{krauterFormalizationAnalysisBPMN2023}

\section{Innovations?}

% \begin{acknowledgments}
% Thanks to the anonymous reviewers for their valuable feedback.
% \end{acknowledgments}

\bibliography{bib}

%%
%% If your work has an appendix, this is the place to put it.
% \appendix

\end{document}

%%
%% End of file

### 2024-06-24 main.tex
gitignore
Add authors

@@
 %% One can fix some overfills
-\sloppy
+% \sloppy
+
+% This was used to mitigate some warnings
+\usepackage[T1]{fontenc}
+\usepackage{lmodern}
 
@@
 
-\title{Instantaneous, Comprehensible, and Fixable Soundness Checking of Realistic BPMN Models}
+% TODO: Rename Rust BPMN Analyzer to BPMN Analyzer 2.0 on my website and maybe somewhere on GitHub.
+\title{BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Anomaly Detection for Realistic BPMN Models}
 
-\author[1]{Tim Kräuter}[
-email=tkra@hvl.no
-]
+\author[1]{Tim Kräuter}
+[email=tkra@hvl.no]
+\author[1]{Patrick Stünkel}
+[email=patrick.stuenkel@hvl.no]
+\author[1]{Adrian Rutle}
+[email=aru@hvl.no]
+\author[1]{Yngve Lamo}
+[email=yla@hvl.no]
+\author[2,1]{Harald König}
+[email=harald.koenig@fhdw.de]
 \address[1]{Western Norway University of Applied Sciences, Bergen, Norway}
+\address[2]{FHDW Hannover, Germany}
 
 \begin{abstract}
-  TBD
+  The tool is available online.
 \end{abstract}
@@
 \section{Introduction}
-\cite{krauterFormalizationAnalysisBPMN2023}
+The tool is available online\footnote{\url{https://timkraeuter.com/bpmn-analyzer-js/}} alongside a video demonstration\footnote{\url{https://www.youtube.com/watch?v=MxXbNUl6IjE}}.
+% Why is it significant for the BPM field?
 
-\section{Innovations?}
+\section{Innovations?} % Main tool description and showing the innovations
+Three main innovations of the tool:
+% Instantaneous
+% Comprehensible
+% Fixable
+
+\section{Maturity of the tool}
+% Scalability tests (instantaneous)
+Improves upon our previous BPMN Analyzer tool~\cite{krauterFormalizationAnalysisBPMN2023}.
+% bpmn.io forum link/mention
 
@@
 % \end{acknowledgments}
+
+\section{Related work?}
+
+\section{Conclusion \& future work}
 

### 2024-06-25 main.tex
Cleanup
Add overview
Add abstract

@@
 
-%%
-%% One can fix some overfills
+% One can fix some overfills
 % \sloppy
@@
 
-%%
-%% Rights management information.
-%% CC-BY is the default license.
+% Rights management information. CC-BY is the default license.
 \copyrightyear{2024}
@@
 
-%%
-%% This command is for the conference information
-\conference{BPM 2024: Demos and Resources,
-  September 01--06, 2024, Krakow, PL}
+\conference{BPM 2024: Demos and Resources, September 01-06, 2024, Krakow, PL}
 
-% TODO: Rename Rust BPMN Analyzer to BPMN Analyzer 2.0 on my website and maybe somewhere on GitHub.
 \title{BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Anomaly Detection for Realistic BPMN Models}
@@
 \author[1]{Patrick Stünkel}
-[email=patrick.stuenkel@hvl.no]
+[email=past@hvl.no] % patrick.stuenkel@hvl.no
 \author[1]{Adrian Rutle}
@@
 \begin{abstract}
-  The tool is available online.
+Many business process models have control-flow anomalies, such as deadlocks or livelocks, which can hinder proper execution.
+In this paper, we introduce our new tool that can instantaneously identify anomalies in BPMN models, make them comprehensible for modelers, and even suggest corrections to resolve them automatically.
+We demonstrate that our tool's detection is instantaneous, i.e., it takes less than 500ms, by benchmarking our tool against synthetic BPMN models with increasing size and state space complexity, as well as realistic models provided in the literature.
+Moreover, the tool directly displays detected anomalies in the model and provides an interactive visualization.
+Additionally, it provides fixes to resolve the anomalies found, which are not currently available in other tools.
+The tool is open-source, modular, extensible, and integrated into a popular BPMN modeling tool.
 \end{abstract}
 
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
 \begin{keywords}
@@
 Verification,
+Control-flow Analysis,
+BPMN model checking,
 Soundness,
@@
 % Details can be found here: https://bpm2024.agh.edu.pl/call-for-demos-and-resources/
+% 5 pages including references
+% Extended version on GitHub and then on Arxiv once submitted
 
@@
 % Why is it significant for the BPM field?
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=\linewidth]{images/overview}
+	\caption{Overview of the tool}
+	\label{fig:overview}
+\end{figure}
 
@@
 Improves upon our previous BPMN Analyzer tool~\cite{krauterFormalizationAnalysisBPMN2023}.
-% bpmn.io forum link/mention
+% bpmn.io forum link/mention: https://forum.bpmn.io/t/automatic-bpmn-control-flow-analysis-and-resolution/11150
 
@@
 \section{Related work?}
+% Could cite my other extended version and put that on arxiv.
 
@@
 
-%%
-%% If your work has an appendix, this is the place to put it.
+% If your work has an appendix, this is the place to put it.
 % \appendix
@@
 \end{document}
-
-%%
-%% End of file

### 2024-06-25 main.tex
Rough conclusion

@@
 
+In this paper, we describe a novel tool that provides instantaneous, comprehensible, and fixable BPMN control-flow anomaly detection and is integrated into a popular BPMN modeling tool.
+We benchmarked our tool against synthetic and realistic BPMN models to demonstrate instantaneous soundness checking.
+We address the three main challenges for providing soundness-checking capabilities to non-expert users as identified in~\cite{fahlandAnalysisDemandInstantaneous2011}.
+First, a model checker must be able to check all or most user-created models, i.e., it must support the most used BPMN elements.
+This is not a problem for most tools, including ours, which has similar capabilities to~\cite{corradiniFormalApproachAnalysis2021}, and we plan to increase our tool's BPMN coverage as needed.
+Second, model checking must be \textit{instantaneous} since long runtimes are unacceptable and often interpreted as tool errors~\cite{fahlandAnalysisDemandInstantaneous2011}.
+Third, the biggest challenge for model checking is \textit{consumability}, i.e., reporting the found violations in a comprehensible user interface.
+Our tool addresses all these challenges and even provides quick fixes for common anomalies.
+The tool is a BPMN-specific model checker written in Rust paired with an intuitive user interface based on the popular \textit{bpmn.io} ecosystem that allows easy extension in the future.
+
 \bibliography{bib}

### 2024-07-03 main.tex
Shrink abstract

@@
 \begin{abstract}
-Many business process models have control-flow anomalies, such as deadlocks or livelocks, which can hinder proper execution.
-In this paper, we introduce our new tool that can instantaneously identify anomalies in BPMN models, make them comprehensible for modelers, and even suggest corrections to resolve them automatically.
-We demonstrate that our tool's detection is instantaneous, i.e., it takes less than 500ms, by benchmarking our tool against synthetic BPMN models with increasing size and state space complexity, as well as realistic models provided in the literature.
-Moreover, the tool directly displays detected anomalies in the model and provides an interactive visualization.
-Additionally, it provides fixes to resolve the anomalies found, which are not currently available in other tools.
-The tool is open-source, modular, extensible, and integrated into a popular BPMN modeling tool.
+% 102 words
+Many business process models have control-flow anomalies, such as deadlocks or livelocks, which hinder proper execution.
+In this paper, we introduce a new tool that can instantaneously identify anomalies in BPMN models, make them understandable for modelers, and suggest corrections to resolve them.
+We demonstrate that detection is instantaneous by benchmarking our tool against synthetic BPMN models with increasing size and state space complexity, as well as realistic models.
+Moreover, the tool directly displays detected anomalies in the model, including an interactive visualization, and suggests fixes to resolve them.
+The tool is open-source, extensible, and integrated into a popular BPMN modeling tool.
 \end{abstract}
@@
 
+% An introduction section, which, among others, should highlight the significance of the tool or resource to the BPM field;
 \section{Introduction}
@@
 
-\section{Innovations?} % Main tool description and showing the innovations
+% Must have section according to the description
+% A section discussing the innovations of the tool or resource to the BPM community and its main characteristics or features
+\section{Innovations} % Main tool description and showing the innovations
 Three main innovations of the tool:

### 2024-07-03 main.tex
Cleanup
Introduction

@@
 \documentclass[
-twocolumn,
-% hf,
+% hf, % <-- Not sure if this should be enabled
 ]{ceurart}
@@
 
-\title{BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Anomaly Detection for Realistic BPMN Models}
+\title{BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Anomaly Detection for BPMN Models}
 
@@
 \maketitle
+% 5 pages including references
 
-% Details can be found here: https://bpm2024.agh.edu.pl/call-for-demos-and-resources/
-% 5 pages including references
 % Extended version on GitHub and then on Arxiv once submitted
@@
 \section{Introduction}
-The tool is available online\footnote{\url{https://timkraeuter.com/bpmn-analyzer-js/}} alongside a video demonstration\footnote{\url{https://www.youtube.com/watch?v=MxXbNUl6IjE}}.
-% Why is it significant for the BPM field?
+
+% Problem statement
+Business Process Modeling Notation (BPMN) is becoming increasingly popular for automating processes and orchestrating people and systems.
+However, many process models suffer from control-flow anomalies, such as deadlocks, livelocks, starvation, and lack of synchronization~\cite{fahlandAnalysisDemandInstantaneous2011}.
+These errors hinder the correct execution of BPMN models and may be detected late in the development process, resulting in elevated costs.
+
+% Solution
+In this paper, we describe a new tool, the \textit{BPMN Analyzer 2.0}\footnote{
+In the following, we will use BPMN Analyzer to refer to the BPMN Analyzer 2.0, not our previous BPMN Analyzer described in \cite{krauterFormalizationAnalysisBPMN2023}.}, for analyzing BPMN process models to detect control-flow anomalies \textit{already} during modeling.
+\autoref{fig:overview} shows an overview of the tool.
+The tool front-end is based on the popular \textit{bpmn.io} ecosystem, while the analysis is implemented in Rust for performance and memory efficiency reasons.
+The BPMN Analyzer is open-source and accessible online\footnote{\url{https://timkraeuter.com/bpmn-analyzer-js/}} alongside a video demonstration\footnote{\url{https://www.youtube.com/watch?v=MxXbNUl6IjE}}~\cite{timkrauterBPM2024Artifacts2024}.
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{images/overview}
-	\caption{Overview of the tool}
+	\includegraphics[width=0.6\linewidth]{images/overview}
+	\caption{Overview of the BPMN Analyzer 2.0}
 	\label{fig:overview}
@@
 
+The tool can check models after each change since analysis is \textit{instantaneous} according to \cite{fahlandAnalysisDemandInstantaneous2011}, i.e., it takes 500ms or less.
+Furthermore, we ensure the results are \textit{comprehensible} by highlighting possible violations directly in the model and displaying an interactive counterexample visualization.
+Finally, the tool suggests \textit{fixes} for the most common soundness violations and can be extended to suggest more fixes in the future.
+However, the BPMN analyzer cannot provide fixes for all possible violations due to the wide variety of possible control-flow anomalies in BPMN models.
+
+% Why is it significant for the BPM field?
+Fahland et al.~\cite{fahlandAnalysisDemandInstantaneous2011} describe \textit{coverage}, \textit{immediacy}, and \textit{consumability} as the main challenges for users unaccustomed to formal analysis methods.
+The BPMN Analyzer addresses all these challenges since it supports the most common BPMN elements used in practice (coverage), provides \textit{instantaneous} results (immediacy), and a \textit{comprehensible} user interface (consumability), even including suggestions of fixes.
+Developers of industrial BPMN solutions also like our tool, especially the End-2-End user journey\footnote{\url{https://forum.bpmn.io/t/automatic-bpmn-control-flow-analysis-and-resolution/11150}}.
+Thus validating our claim of a UI that is understandable for users unfamiliar with formal analysis methods.
+
+% Paper structure
+In the remainder of the paper, we describe how instantaneous, comprehensible, and fixable anomaly detection is achieved in \autoref{sec:innovations}.
+Then, we discuss the maturity of our tool in \autoref{sec:maturity} before presenting related work in \autoref{sec:related-work}.
+Finally, we conclude in \autoref{sec:conclusion}.
+
 % Must have section according to the description
 % A section discussing the innovations of the tool or resource to the BPM community and its main characteristics or features
-\section{Innovations} % Main tool description and showing the innovations
+\section{Innovations} \label{sec:innovations} % Main tool description and showing the innovations
 Three main innovations of the tool:
@@
 
-\section{Maturity of the tool}
-% Scalability tests (instantaneous)
+% They also want this section
+\section{Maturity of the tool} \label{sec:maturity}
+% Discuss/highlight the implementation: Test cases, static analysis etc. industrial standard! ;)
+% Scalability tests (instantaneous) --> Generated models are public including our tool for future direct comparisons
 Improves upon our previous BPMN Analyzer tool~\cite{krauterFormalizationAnalysisBPMN2023}.
+
 % bpmn.io forum link/mention: https://forum.bpmn.io/t/automatic-bpmn-control-flow-analysis-and-resolution/11150
 
-% \begin{acknowledgments}
-% Thanks to the anonymous reviewers for their valuable feedback.
-% \end{acknowledgments}
+% TODO: Update DOI link to fit the extended version on arxiv
+% Extended version: \cite{krauterInstantaneousComprehensibleFixable2024}
 
-\section{Related work?}
-% Could cite my other extended version and put that on arxiv.
+Artifacts: \cite{timkrauterBPM2024Artifacts2024}
 
-\section{Conclusion \& future work}
+\section{Related work?} \label{sec:related-work}
+
+% Breakdown of BPMN coverage: https://github.com/timKraeuter/rust_bpmn_analyzer?tab=readme-ov-file#bpmn-coverage
+
+\section{Conclusion \& future work} \label{sec:conclusion}
 
@@
 
+% \begin{acknowledgments}
+% Thanks to the anonymous reviewers for their valuable feedback.
+% \end{acknowledgments}
+
 \bibliography{bib}
 
-% If your work has an appendix, this is the place to put it.
-% \appendix
-
 \end{document}

### 2024-07-04 main.tex
Next section

@@
 
+% TODO: Soundness vs anomaly detection? Maybe use soundness and say later that in the UI, it's not called soundness!
+
 \maketitle
@@
 
-% Extended version on GitHub and then on Arxiv once submitted
-
-% An introduction section, which, among others, should highlight the significance of the tool or resource to the BPM field;
 \section{Introduction}
@@
 \section{Innovations} \label{sec:innovations} % Main tool description and showing the innovations
-Three main innovations of the tool:
+The BPMN Analyzer has three main innovations: \textbf{instantaneous}, \textbf{comprehensible}, and \textbf{fixable} anomaly detection.
+In this section, we will present the innovations, and more details can be found in our extended paper \cite{krauterInstantaneousComprehensibleFixable2024}.
 % Instantaneous
@@
 \section{Maturity of the tool} \label{sec:maturity}
-% Discuss/highlight the implementation: Test cases, static analysis etc. industrial standard! ;)
-% Scalability tests (instantaneous) --> Generated models are public including our tool for future direct comparisons
-Improves upon our previous BPMN Analyzer tool~\cite{krauterFormalizationAnalysisBPMN2023}.
+% Discuss/highlight the implementation: Test cases, static analysis, etc., industrial standard! ;)
+% Scalability tests (instantaneous) --> Generated models are public, including our tool for future direct comparisons
+The BPMN Analyzer is our newest tool, incorporating many findings from our previous work \cite{krauterFormalizationAnalysisBPMN2023} while focusing on instantaneous and understandable anomaly detection.
 
@@
 
-% TODO: Update DOI link to fit the extended version on arxiv
+% TODO: Update the DOI link to fit the extended version on arxiv
 % Extended version: \cite{krauterInstantaneousComprehensibleFixable2024}

### 2024-07-04 main.tex
Anomaly to error

@@
 
-\title{BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Anomaly Detection for BPMN Models}
+\title{BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Control-Flow Analysis for BPMN Models}
 
@@
 % 102 words
-Many business process models have control-flow anomalies, such as deadlocks or livelocks, which hinder proper execution.
-In this paper, we introduce a new tool that can instantaneously identify anomalies in BPMN models, make them understandable for modelers, and suggest corrections to resolve them.
+Many business process models contain control-flow errors, such as deadlocks or livelocks, which hinder proper execution.
+In this paper, we introduce a new tool that can instantaneously identify control-flow errors in BPMN models, make them understandable for modelers, and suggest corrections to resolve them.
 We demonstrate that detection is instantaneous by benchmarking our tool against synthetic BPMN models with increasing size and state space complexity, as well as realistic models.
-Moreover, the tool directly displays detected anomalies in the model, including an interactive visualization, and suggests fixes to resolve them.
+Moreover, the tool directly displays detected errors in the model, including an interactive visualization, and suggests fixes to resolve them.
 The tool is open-source, extensible, and integrated into a popular BPMN modeling tool.
@@
 
-% TODO: Soundness vs anomaly detection? Maybe use soundness and say later that in the UI, it's not called soundness!
-
 \maketitle
@@
 Business Process Modeling Notation (BPMN) is becoming increasingly popular for automating processes and orchestrating people and systems.
-However, many process models suffer from control-flow anomalies, such as deadlocks, livelocks, starvation, and lack of synchronization~\cite{fahlandAnalysisDemandInstantaneous2011}.
+However, many process models suffer from control-flow errors, such as deadlocks, livelocks, starvation, and lack of synchronization~\cite{fahlandAnalysisDemandInstantaneous2011}.
 These errors hinder the correct execution of BPMN models and may be detected late in the development process, resulting in elevated costs.
@@
 In this paper, we describe a new tool, the \textit{BPMN Analyzer 2.0}\footnote{
-In the following, we will use BPMN Analyzer to refer to the BPMN Analyzer 2.0, not our previous BPMN Analyzer described in \cite{krauterFormalizationAnalysisBPMN2023}.}, for analyzing BPMN process models to detect control-flow anomalies \textit{already} during modeling.
+In the following, we will use BPMN Analyzer to refer to the BPMN Analyzer 2.0, not our previous BPMN Analyzer described in \cite{krauterFormalizationAnalysisBPMN2023}.}, for analyzing BPMN process models to detect control-flow errors \textit{already} during modeling.
 \autoref{fig:overview} shows an overview of the tool.
@@
 Finally, the tool suggests \textit{fixes} for the most common soundness violations and can be extended to suggest more fixes in the future.
-However, the BPMN analyzer cannot provide fixes for all possible violations due to the wide variety of possible control-flow anomalies in BPMN models.
+However, the BPMN analyzer cannot provide fixes for all possible violations due to the wide variety of possible control-flow errors in BPMN models.
 
@@
 % Paper structure
-In the remainder of the paper, we describe how instantaneous, comprehensible, and fixable anomaly detection is achieved in \autoref{sec:innovations}.
+In the remainder of the paper, we describe how instantaneous, comprehensible, and fixable control-flow error detection is achieved in \autoref{sec:innovations}.
 Then, we discuss the maturity of our tool in \autoref{sec:maturity} before presenting related work in \autoref{sec:related-work}.
@@
 \section{Innovations} \label{sec:innovations} % Main tool description and showing the innovations
-The BPMN Analyzer has three main innovations: \textbf{instantaneous}, \textbf{comprehensible}, and \textbf{fixable} anomaly detection.
+The BPMN Analyzer has three main innovations: \textbf{instantaneous}, \textbf{comprehensible}, and \textbf{fixable} control-flow error detection.
 In this section, we will present the innovations, and more details can be found in our extended paper \cite{krauterInstantaneousComprehensibleFixable2024}.
@@
 % Scalability tests (instantaneous) --> Generated models are public, including our tool for future direct comparisons
-The BPMN Analyzer is our newest tool, incorporating many findings from our previous work \cite{krauterFormalizationAnalysisBPMN2023} while focusing on instantaneous and understandable anomaly detection.
+The BPMN Analyzer is our newest tool, incorporating many findings from our previous work \cite{krauterFormalizationAnalysisBPMN2023} while focusing on instantaneous and understandable error detection.
 
@@
 
-In this paper, we describe a novel tool that provides instantaneous, comprehensible, and fixable BPMN control-flow anomaly detection and is integrated into a popular BPMN modeling tool.
+In this paper, we describe a novel tool that provides instantaneous, comprehensible, and fixable BPMN control-flow error detection and is integrated into a popular BPMN modeling tool.
 We benchmarked our tool against synthetic and realistic BPMN models to demonstrate instantaneous soundness checking.
@@
 Second, model checking must be \textit{instantaneous} since long runtimes are unacceptable and often interpreted as tool errors~\cite{fahlandAnalysisDemandInstantaneous2011}.
-Third, the biggest challenge for model checking is \textit{consumability}, i.e., reporting the found violations in a comprehensible user interface.
-Our tool addresses all these challenges and even provides quick fixes for common anomalies.
+Third, the biggest challenge for model checking is \textit{consumability}, i.e., reporting the found errors in a comprehensible user interface.
+Our tool addresses all these challenges and even provides quick fixes for common errors.
 The tool is a BPMN-specific model checker written in Rust paired with an intuitive user interface based on the popular \textit{bpmn.io} ecosystem that allows easy extension in the future.

### 2024-07-04 main.tex
Instantaneous

@@
 \usepackage{lmodern}
+% Modern tables + extra stuff workaround
+\selectcolormodel{natural}
+\usepackage{ninecolors}
+\selectcolormodel{rgb}
+\usepackage{tabularray}
 
@@
 
-\title{BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Control-Flow Analysis for BPMN Models}
+\title{BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Control Flow Analysis for BPMN Models}
 
@@
 % 102 words
-Many business process models contain control-flow errors, such as deadlocks or livelocks, which hinder proper execution.
-In this paper, we introduce a new tool that can instantaneously identify control-flow errors in BPMN models, make them understandable for modelers, and suggest corrections to resolve them.
+Many business process models contain control flow errors, such as deadlocks or livelocks, which hinder proper execution.
+In this paper, we introduce a new tool that can instantaneously identify control flow errors in BPMN models, make them understandable for modelers, and suggest corrections to resolve them.
 We demonstrate that detection is instantaneous by benchmarking our tool against synthetic BPMN models with increasing size and state space complexity, as well as realistic models.
@@
 Verification,
-Control-flow Analysis,
+Control flow analysis,
 BPMN model checking,
@@
 Business Process Modeling Notation (BPMN) is becoming increasingly popular for automating processes and orchestrating people and systems.
-However, many process models suffer from control-flow errors, such as deadlocks, livelocks, starvation, and lack of synchronization~\cite{fahlandAnalysisDemandInstantaneous2011}.
+However, many process models suffer from control flow errors, such as deadlocks, livelocks, starvation, and lack of synchronization~\cite{fahlandAnalysisDemandInstantaneous2011}.
 These errors hinder the correct execution of BPMN models and may be detected late in the development process, resulting in elevated costs.
@@
 In this paper, we describe a new tool, the \textit{BPMN Analyzer 2.0}\footnote{
-In the following, we will use BPMN Analyzer to refer to the BPMN Analyzer 2.0, not our previous BPMN Analyzer described in \cite{krauterFormalizationAnalysisBPMN2023}.}, for analyzing BPMN process models to detect control-flow errors \textit{already} during modeling.
+In the following, we will use BPMN Analyzer to refer to the BPMN Analyzer 2.0, not our previous BPMN Analyzer described in \cite{krauterFormalizationAnalysisBPMN2023}.}, for analyzing BPMN process models to detect control flow errors \textit{already} during modeling.
 \autoref{fig:overview} shows an overview of the tool.
 The tool front-end is based on the popular \textit{bpmn.io} ecosystem, while the analysis is implemented in Rust for performance and memory efficiency reasons.
-The BPMN Analyzer is open-source and accessible online\footnote{\url{https://timkraeuter.com/bpmn-analyzer-js/}} alongside a video demonstration\footnote{\url{https://www.youtube.com/watch?v=MxXbNUl6IjE}}~\cite{timkrauterBPM2024Artifacts2024}.
+The BPMN Analyzer is open-source and accessible online\footnote{\url{https://timkraeuter.com/bpmn-analyzer-js/}} alongside a video demonstration\footnote{\url{https://www.youtube.com/watch?v=MxXbNUl6IjE}}~\cite{krauterInstantaneousComprehensibleFixable2024}.
 
@@
 Finally, the tool suggests \textit{fixes} for the most common soundness violations and can be extended to suggest more fixes in the future.
-However, the BPMN analyzer cannot provide fixes for all possible violations due to the wide variety of possible control-flow errors in BPMN models.
+However, the BPMN analyzer cannot provide fixes for all possible violations due to the wide variety of possible control flow errors in BPMN models.
 
@@
 The BPMN Analyzer addresses all these challenges since it supports the most common BPMN elements used in practice (coverage), provides \textit{instantaneous} results (immediacy), and a \textit{comprehensible} user interface (consumability), even including suggestions of fixes.
-Developers of industrial BPMN solutions also like our tool, especially the End-2-End user journey\footnote{\url{https://forum.bpmn.io/t/automatic-bpmn-control-flow-analysis-and-resolution/11150}}.
+Developers of industrial BPMN solutions also like our tool, especially the End-2-End user journey\footnote{\url{https://forum.bpmn.io/t/automatic-bpmn-control flow-analysis-and-resolution/11150}}.
 Thus validating our claim of a UI that is understandable for users unfamiliar with formal analysis methods.
@@
 % Paper structure
-In the remainder of the paper, we describe how instantaneous, comprehensible, and fixable control-flow error detection is achieved in \autoref{sec:innovations}.
+In the remainder of the paper, we describe how instantaneous, comprehensible, and fixable control flow error detection is achieved in \autoref{sec:innovations}.
 Then, we discuss the maturity of our tool in \autoref{sec:maturity} before presenting related work in \autoref{sec:related-work}.
@@
 \section{Innovations} \label{sec:innovations} % Main tool description and showing the innovations
-The BPMN Analyzer has three main innovations: \textbf{instantaneous}, \textbf{comprehensible}, and \textbf{fixable} control-flow error detection.
+The BPMN Analyzer has three main innovations: \textbf{instantaneous}, \textbf{comprehensible}, and \textbf{fixable} control flow error detection.
 In this section, we will present the innovations, and more details can be found in our extended paper \cite{krauterInstantaneousComprehensibleFixable2024}.
-% Instantaneous
-% Comprehensible
-% Fixable
+
+\subsection{Instantaneous Analysis}
+
+We demonstrate instantaneous control flow analysis by benchmarking our tool in \textit{three} different scenarios.
+For all our benchmarks, we use the hyperfine benchmarking tool~\cite{peterHyperfine2023} (version 1.18.0), which calculates the average runtime when executing each control flow analysis ten or more times.
+The benchmarks were run on Ubuntu 22.04.4 with an AMD Ryzen 7700X processor (4.5GHz) and 32 GB of RAM.
+All used BPMN models, our tools to generate them, and benchmarking scripts to run them are available in~\cite{krauterInstantaneousComprehensibleFixable2024}.
+
+\textbf{First}, we benchmarked how our tool handles \textbf{BPMN models of growing size}.
+We generated 500 synthetic BPMN models starting with five elements up to 4000 elements, increasing linearly in size.
+The models repeatedly contain three activities and an exclusive/parallel block with two branches containing one activity per branch (more details in~\cite{krauterInstantaneousComprehensibleFixable2024}).
+The BPMN Analyzer spends from 1 ms up to 9 ms for the BPMN models compared to 0.7 s up to 14 s in our previous tool~\cite{krauterHigherorderTransformationApproach2023}.
+In summary, the linear growth of the models leads to a linear growth in state space and, consequently, a linear growth in runtime.
+
+\textbf{Second}, we benchmarked the tool against a synthetic data set of models that lead to a state space explosion.
+This represents a \textit{worst case} scenario for formal analysis.
+We generated a data set of models~\cite{krauterInstantaneousComprehensibleFixable2024} with a growing number of parallel branches with increasing length, similar to~\cite{corradiniFormalApproachAnalysis2021}.
+\autoref{tab:parallel-branches-benchmark} shows the average runtime of our tool when analyzing these models.
+The BPMN Analyzer explores the entire state space while simultaneously analyzing the control flow, i.e., verifying soundness properties.
+
+\begin{table}[h]
+	\centering
+	\caption{Benchmark results for models with varying parallel branches}
+	\label{tab:parallel-branches-benchmark}
+	\SetTblrInner{colsep=2pt}
+	\begin{tblr}{
+			column{1-X} = {c},
+			column{Y-Z} = {r},
+			hline{1, 2, Z} = {-}{1.2pt, solid}, % Z is the last row/column
+			hline{6, 7} = {-}{dashed},
+			vline{2-Y} = {2-Z}{solid}, % Y is the second to last row/column
+		}
+		\textbf{Branches} & \textbf{Branch Length} &\textbf{Runtime} & \textbf{States} \\
+		15 & 1 & 161 ms& 32.771 \\
+		16 & 1 & 360 ms& 65.539 \\
+		17 & 1 & 790 ms& 131.075 \\
+		20 & 1 & 8.803 ms& 1.048.579 \\
+		5 & 5 & 14 ms& 7.779 \\
+		3 & 20 & 11 ms& 9.264 \\
+	\end{tblr}
+\end{table}
+
+The models' state space grows exponentially, leading to the same order of growth in runtime.
+Our analysis is not instantaneous anymore when approaching 17 parallel branches of length 1 (see \autoref{tab:parallel-branches-benchmark}).
+However, analysis is still instantaneous for more reasonable models with five parallel branches of length 5 or 3 branches of length 20.
+Other tools report 2-3s of runtime for most soundness properties and 30s for a model with five parallel branches~\cite{corradiniFormalApproachAnalysis2021}, which took us only milliseconds.
+
+\textbf{Third}, we applied our tool to eight \textbf{realistic models}, where three models (e001, e002, e020) are taken from~\cite{houhouFirstOrderLogicVerification2022}, and the remaining five models are part of the Camunda BPMN for research repository\footnote{\url{https://github.com/camunda/bpmn-for-research} \label{footnote:camundaResearch}}.
+The BPMN Analyzer takes 1-10ms for e001, e002, and e020 ~\cite{krauterInstantaneousComprehensibleFixable2024} while~\cite{houhouFirstOrderLogicVerification2022} and~\cite{krauterFormalizationAnalysisBPMN2023} report 3.66-10.26s and 1-1.75s.
+The benchmarks in~\cite{krauterFormalizationAnalysisBPMN2023} were run on the same hardware, while the machine used in~\cite{houhouFirstOrderLogicVerification2022} was slightly less powerful.
+
+\subsection{Comprehensible Analysis}
+
+\subsection{Fixable Analysis}
 
@@
 
-% bpmn.io forum link/mention: https://forum.bpmn.io/t/automatic-bpmn-control-flow-analysis-and-resolution/11150
+% bpmn.io forum link/mention: https://forum.bpmn.io/t/automatic-bpmn-control flow-analysis-and-resolution/11150
 
@@
 
-Artifacts: \cite{timkrauterBPM2024Artifacts2024}
+Artifacts: \cite{krauterInstantaneousComprehensibleFixable2024}
 
@@
 
-In this paper, we describe a novel tool that provides instantaneous, comprehensible, and fixable BPMN control-flow error detection and is integrated into a popular BPMN modeling tool.
+In this paper, we describe the novel BPMN Analyzer tool that provides instantaneous, comprehensible, and fixable BPMN control flow error detection and is integrated into a popular BPMN modeling tool.
 We benchmarked our tool against synthetic and realistic BPMN models to demonstrate instantaneous soundness checking.

### 2024-07-05 main.tex
More or less done?

@@
 \title{BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Control Flow Analysis for BPMN Models}
+% TODO: Update the DOI link to fit the extended version on arxiv
 
@@
 In this paper, we describe a new tool, the \textit{BPMN Analyzer 2.0}\footnote{
-In the following, we will use BPMN Analyzer to refer to the BPMN Analyzer 2.0, not our previous BPMN Analyzer described in \cite{krauterFormalizationAnalysisBPMN2023}.}, for analyzing BPMN process models to detect control flow errors \textit{already} during modeling.
+In the following, we will use BPMN Analyzer to refer to the BPMN Analyzer 2.0, not our previous BPMN Analyzer described in~\cite{krauterFormalizationAnalysisBPMN2023}.}, for analyzing BPMN process models to detect control flow errors \textit{already} during modeling.
+% TODO: Maybe give concrete examples of what we can check!
 \autoref{fig:overview} shows an overview of the tool.
@@
 
-The tool can check models after each change since analysis is \textit{instantaneous} according to \cite{fahlandAnalysisDemandInstantaneous2011}, i.e., it takes 500ms or less.
+The tool can check models after each change since analysis is \textit{instantaneous} according to~\cite{fahlandAnalysisDemandInstantaneous2011}, i.e., it takes 500ms or less.
 Furthermore, we ensure the results are \textit{comprehensible} by highlighting possible violations directly in the model and displaying an interactive counterexample visualization.
 Finally, the tool suggests \textit{fixes} for the most common soundness violations and can be extended to suggest more fixes in the future.
-However, the BPMN analyzer cannot provide fixes for all possible violations due to the wide variety of possible control flow errors in BPMN models.
 
@@
 The BPMN Analyzer addresses all these challenges since it supports the most common BPMN elements used in practice (coverage), provides \textit{instantaneous} results (immediacy), and a \textit{comprehensible} user interface (consumability), even including suggestions of fixes.
-Developers of industrial BPMN solutions also like our tool, especially the End-2-End user journey\footnote{\url{https://forum.bpmn.io/t/automatic-bpmn-control flow-analysis-and-resolution/11150}}.
+Developers of industrial BPMN solutions also like our tool, especially the End-2-End user journey~\cite{krauterInstantaneousComprehensibleFixable2024}.
 Thus validating our claim of a UI that is understandable for users unfamiliar with formal analysis methods.
@@
 The BPMN Analyzer has three main innovations: \textbf{instantaneous}, \textbf{comprehensible}, and \textbf{fixable} control flow error detection.
-In this section, we will present the innovations, and more details can be found in our extended paper \cite{krauterInstantaneousComprehensibleFixable2024}.
+In this section, we will present the innovations, and more details can be found in our extended paper~\cite{krauterInstantaneousComprehensibleFixable2024}.
 
@@
 The benchmarks in~\cite{krauterFormalizationAnalysisBPMN2023} were run on the same hardware, while the machine used in~\cite{houhouFirstOrderLogicVerification2022} was slightly less powerful.
+To summarize, we believe our analysis is instantaneous for nearly all models since most models have relatively small state spaces (less than 1000 states, see~\cite{fahlandAnalysisDemandInstantaneous2011}).
 
 \subsection{Comprehensible Analysis}
+We implemented two features to make control flow analysis understandable for everyone. 
+% Highlighting
+\textbf{First}, we highlight the problematic elements that cause control flow errors by directly attaching red overlays to them in the BPMN model.
+In addition, there is a summary panel stating which if any errors are found.
+
+% TODO: A screenshot of the tool would be nice here!
+
+% Counterexample
+\textbf{Second}, we use \textit{tokens} to \textit{interactively} visualize errors, i.e., we show an execution leading to the error.
+Our analysis provides sample executions leading to the possible control-flow errors, which we visualize directly in the BPMN editor by showing how tokens move from the process start to an erroneous state.
+We are unaware of other tools that visualize errors directly in the editor and allow for interactions, such as stopping/resuming, restarting, and speeding up the execution.
 
 \subsection{Fixable Analysis}
+In addition to detecting, highlighting, and visualizing control flow errors, the BPMN Analyzer suggests fixes similar to \textit{quick fixes} in Integrated Development Environments.
+Quick fixes cannot be provided for all errors, but we currently cover some patterns leading to deadlocks, lack of synchronization, message starvation, and reused end events.
+The quick fixes we support are described in detail in~\cite{krauterInstantaneousComprehensibleFixable2024} and can be extended independently of the formal analysis.
+We are unaware of other tools that offer fixes for identified control-flow errors.
 
@@
 \section{Maturity of the tool} \label{sec:maturity}
-% Discuss/highlight the implementation: Test cases, static analysis, etc., industrial standard! ;)
+The BPMN Analyzer is our newest tool, incorporating many findings from our previous work~\cite{krauterFormalizationAnalysisBPMN2023} while focusing on instantaneous and understandable error detection.
+The tool is open-source~\cite{krauterInstantaneousComprehensibleFixable2024}, and we aim to achieve high code quality by employing industry best practices such as rigorous static analysis, testing, and consistent formatting.
+Furthermore, we demonstrated the tool to companies in the BPMN process orchestration space and received positive initial feedback, as described in the introduction.
+
 % Scalability tests (instantaneous) --> Generated models are public, including our tool for future direct comparisons
-The BPMN Analyzer is our newest tool, incorporating many findings from our previous work \cite{krauterFormalizationAnalysisBPMN2023} while focusing on instantaneous and understandable error detection.
+As described in the previous section, we benchmarked our tool runtime in three scenarios.
+The tool can check most models instantaneously, and we provide more details, including scripts and data needed to reproduce our results in~\cite{krauterInstantaneousComprehensibleFixable2024}.
 
-% bpmn.io forum link/mention: https://forum.bpmn.io/t/automatic-bpmn-control flow-analysis-and-resolution/11150
+\section{Related work} \label{sec:related-work}
 
-% TODO: Update the DOI link to fit the extended version on arxiv
-% Extended version: \cite{krauterInstantaneousComprehensibleFixable2024}
+BPMN analysis tools or formalizations are typically compared by their \textbf{coverage} of BPMN elements~\cite{krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022}.
+Our tool already supports the common BPMN elements~\cite{krauterInstantaneousComprehensibleFixable2024}, and we aim for coverage similar to popular BPMN process orchestration platforms such as Camunda.
+% Breakdown of BPMN coverage: https://github.com/timKraeuter/rust_bpmn_analyzer?tab=readme-ov-file#bpmn-coverage
+However, we agree with~\cite{fahlandAnalysisDemandInstantaneous2011} that \textbf{analysis runtime} and \textbf{understandability} are the main issues that hinder the wide adoption of formal analysis tools outside academia.
 
-Artifacts: \cite{krauterInstantaneousComprehensibleFixable2024}
-
-\section{Related work?} \label{sec:related-work}
-
-% Breakdown of BPMN coverage: https://github.com/timKraeuter/rust_bpmn_analyzer?tab=readme-ov-file#bpmn-coverage
+The BPMN Analyzer has comparable BPMN element coverage to~\cite{corradiniFormalApproachAnalysis2021} but is still missing some elements when compared to~\cite{krauterFormalizationAnalysisBPMN2023}, which are currently on the roadmap.
+In addition, we demonstrated the instantaneous analysis of our tool, which outperforms other tools~\cite{krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022} as described in \autoref{sec:innovations}.
+Finally, we have only received positive feedback regarding the tool's usability.
 

### 2024-07-05 main.tex
Fixes

@@
 We demonstrate instantaneous control flow analysis by benchmarking our tool in \textit{three} different scenarios.
-For all our benchmarks, we use the hyperfine benchmarking tool~\cite{peterHyperfine2023} (version 1.18.0), which calculates the average runtime when executing each control flow analysis ten or more times.
-The benchmarks were run on Ubuntu 22.04.4 with an AMD Ryzen 7700X processor (4.5GHz) and 32 GB of RAM.
+For all our benchmarks, we use the hyperfine benchmarking tool (version 1.18.0), which calculates the average runtime when executing each control flow analysis ten or more times.
+The benchmarks were run on Ubuntu 22.04.4 with an AMD Ryzen 7700X processor (4.5GHz) and 32 GB of RAM (5600 MHz).
 All used BPMN models, our tools to generate them, and benchmarking scripts to run them are available in~\cite{krauterInstantaneousComprehensibleFixable2024}.
@@
 The models repeatedly contain three activities and an exclusive/parallel block with two branches containing one activity per branch (more details in~\cite{krauterInstantaneousComprehensibleFixable2024}).
-The BPMN Analyzer spends from 1 ms up to 9 ms for the BPMN models compared to 0.7 s up to 14 s in our previous tool~\cite{krauterHigherorderTransformationApproach2023}.
+The BPMN Analyzer spends from 1 ms up to 9 ms for the BPMN models compared to 0.7 s up to 14 s in our previous tool~\cite{krauterFormalizationAnalysisBPMN2023}.
 In summary, the linear growth of the models leads to a linear growth in state space and, consequently, a linear growth in runtime.
@@
 
-The BPMN Analyzer has comparable BPMN element coverage to~\cite{corradiniFormalApproachAnalysis2021} but is still missing some elements when compared to~\cite{krauterFormalizationAnalysisBPMN2023}, which are currently on the roadmap.
-In addition, we demonstrated the instantaneous analysis of our tool, which outperforms other tools~\cite{krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022} as described in \autoref{sec:innovations}.
+Our tool has comparable BPMN element coverage to~\cite{corradiniFormalApproachAnalysis2021} but is still missing some elements when compared to~\cite{krauterFormalizationAnalysisBPMN2023}, which are currently on the roadmap.
+In addition, we demonstrated the instantaneous analysis of the BPMN Analyzer, which outperforms other tools~\cite{krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022} as described in \autoref{sec:innovations}.
 Finally, we have only received positive feedback regarding the tool's usability.
 
-\section{Conclusion \& future work} \label{sec:conclusion}
+\section{Conclusion} \label{sec:conclusion}
 
-In this paper, we describe the novel BPMN Analyzer tool that provides instantaneous, comprehensible, and fixable BPMN control flow error detection and is integrated into a popular BPMN modeling tool.
+In this paper, we describe the novel \textit{BPMN Analyzer} that provides instantaneous, comprehensible, and fixable BPMN control flow error detection and is integrated into a popular BPMN modeling tool.
 We benchmarked our tool against synthetic and realistic BPMN models to demonstrate instantaneous soundness checking.
-We address the three main challenges for providing soundness-checking capabilities to non-expert users as identified in~\cite{fahlandAnalysisDemandInstantaneous2011}.
-First, a model checker must be able to check all or most user-created models, i.e., it must support the most used BPMN elements.
-This is not a problem for most tools, including ours, which has similar capabilities to~\cite{corradiniFormalApproachAnalysis2021}, and we plan to increase our tool's BPMN coverage as needed.
-Second, model checking must be \textit{instantaneous} since long runtimes are unacceptable and often interpreted as tool errors~\cite{fahlandAnalysisDemandInstantaneous2011}.
-Third, the biggest challenge for model checking is \textit{consumability}, i.e., reporting the found errors in a comprehensible user interface.
-Our tool addresses all these challenges and even provides quick fixes for common errors.
-The tool is a BPMN-specific model checker written in Rust paired with an intuitive user interface based on the popular \textit{bpmn.io} ecosystem that allows easy extension in the future.
+We address the three main challenges: \textit{coverage}, \textit{immediacy}, and \textit{consumability} for providing formal analysis to non-expert users as identified in~\cite{fahlandAnalysisDemandInstantaneous2011}.
+In addition, our tool provides quick fixes for common patterns leading to control flow errors.
+One can understand the BPMN Analyzer as a BPMN-specific model checker, implemented in Rust paired with an intuitive user interface based on the popular \textit{bpmn.io} ecosystem that allows easy extension in the future.
 

### 2024-07-05 main.tex
Add tool screenshots

@@
 \documentclass[
+twocolumn
 % hf, % <-- Not sure if this should be enabled
@@
 In this paper, we describe a new tool, the \textit{BPMN Analyzer 2.0}\footnote{
-In the following, we will use BPMN Analyzer to refer to the BPMN Analyzer 2.0, not our previous BPMN Analyzer described in~\cite{krauterFormalizationAnalysisBPMN2023}.}, for analyzing BPMN process models to detect control flow errors \textit{already} during modeling.
+In the following, we will use BPMN Analyzer to refer to the BPMN Analyzer 2.0, not our previous BPMN Analyzer described in~\cite{krauterHigherorderTransformationApproach2024}.}, for analyzing BPMN process models to detect control flow errors \textit{already} during modeling.
 % TODO: Maybe give concrete examples of what we can check!
@@
 	\centering
-	\includegraphics[width=0.6\linewidth]{images/overview}
+	\includegraphics[width=1\linewidth]{images/overview}
 	\caption{Overview of the BPMN Analyzer 2.0}
@@
 We demonstrate instantaneous control flow analysis by benchmarking our tool in \textit{three} different scenarios.
-For all our benchmarks, we use the hyperfine benchmarking tool (version 1.18.0), which calculates the average runtime when executing each control flow analysis ten or more times.
+For all our benchmarks, we use the hyperfine benchmarking tool \cite{peterHyperfine2023} (version 1.18.0), which calculates the average runtime when executing each control flow analysis ten or more times.
 The benchmarks were run on Ubuntu 22.04.4 with an AMD Ryzen 7700X processor (4.5GHz) and 32 GB of RAM (5600 MHz).
@@
 	\centering
-	\caption{Benchmark results for models with varying parallel branches}
+	\caption{Benchmark results of the parallel branches models}
 	\label{tab:parallel-branches-benchmark}
@@
 			hline{1, 2, Z} = {-}{1.2pt, solid}, % Z is the last row/column
-			hline{6, 7} = {-}{dashed},
+			hline{8, 10} = {-}{dashed},
 			vline{2-Y} = {2-Z}{solid}, % Y is the second to last row/column
@@
 		\textbf{Branches} & \textbf{Branch Length} &\textbf{Runtime} & \textbf{States} \\
+		5 & 1 & 1 ms& 35 \\
+		10 & 1 & 3 ms& 1.027 \\
 		15 & 1 & 161 ms& 32.771 \\
@@
 		20 & 1 & 8.803 ms& 1.048.579 \\
+		5 & 3 & 3 ms& 1.027 \\
 		5 & 5 & 14 ms& 7.779 \\
+		3 & 10 & 2 ms& 1.334 \\
 		3 & 20 & 11 ms& 9.264 \\
@@
 \textbf{Third}, we applied our tool to eight \textbf{realistic models}, where three models (e001, e002, e020) are taken from~\cite{houhouFirstOrderLogicVerification2022}, and the remaining five models are part of the Camunda BPMN for research repository\footnote{\url{https://github.com/camunda/bpmn-for-research} \label{footnote:camundaResearch}}.
+\autoref{tab:realistic-models-benchmark} shows the average runtime and number of states for each model.
+
+\begin{table}[h]
+	\centering
+	\caption{Benchmark results of the realistic BPMN models}
+	\label{tab:realistic-models-benchmark}
+	\SetTblrInner{colsep=2pt}
+	\begin{tblr}{
+			column{Y-Z} = {r},
+			hline{1, 2, Z} = {-}{1.2pt, solid}, % Z is the last row/column
+			hline{5} = {-}{dashed},
+			vline{2-Y} = {2-Z}{solid}, % Y is the second to last row/column
+		}
+		\textbf{Model name} &\textbf{Runtime} & \textbf{States} \\
+		e001~\cite{houhouFirstOrderLogicVerification2022} & 1 ms & 39 \\
+		e002~\cite{houhouFirstOrderLogicVerification2022} & 1 ms & 39 \\
+		e020~\cite{houhouFirstOrderLogicVerification2022} & 10 ms & 5356 \\
+		credit-scoring-async\footref{footnote:camundaResearch} & 1 ms & 60 \\
+		credit-scoring-sync\footref{footnote:camundaResearch} & 1 ms & 140 \\
+		dispatch-of-goods\footref{footnote:camundaResearch} & 1 ms & 103\\
+		recourse\footref{footnote:camundaResearch} & 1 ms & 77 \\
+		self-service-restaurant\footref{footnote:camundaResearch} & 1 ms & 190 \\
+	\end{tblr}
+\end{table}
+
 The BPMN Analyzer takes 1-10ms for e001, e002, and e020 ~\cite{krauterInstantaneousComprehensibleFixable2024} while~\cite{houhouFirstOrderLogicVerification2022} and~\cite{krauterFormalizationAnalysisBPMN2023} report 3.66-10.26s and 1-1.75s.
@@
 \textbf{First}, we highlight the problematic elements that cause control flow errors by directly attaching red overlays to them in the BPMN model.
-In addition, there is a summary panel stating which if any errors are found.
-
-% TODO: A screenshot of the tool would be nice here!
+In addition, there is a summary panel in the top-right stating if any errors are found.
 
@@
 
+% Describe the figure.
+In \autoref{fig:counterexample}, the visualization has been \textit{paused} just before an \textit{unsafe} state was reached.
+One token is already located at the sequence flow, which is marked, while a second token is currently waiting at the exclusive gateway \textsf{e1}.
+The visualization can be resumed or restarted using the play and restart button on the left side.
+When resumed, the gateway \textsf{e1} will execute, resulting in two tokens at the subsequent sequence flow, i.e., an unsafe execution state.
+In addition, one can control the visualization speed using the bottom buttons next to the speedometer.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=1\linewidth]{images/counter-example}
+	\caption{Interactive \textit{erroneous execution} shown in the BPMN Analyzer}
+	\label{fig:counterexample}
+\end{figure}
+
 \subsection{Fixable Analysis}
@@
 We are unaware of other tools that offer fixes for identified control-flow errors.
+
+For example, \autoref{fig:quick-fixes} shows a screenshot of our tool, where quick fixes are depicted as green overlays containing a light bulb icon.
+A user can apply a quick fix by clicking on a green overlay and instantly see the changes regarding control flow errors.
+If unhappy with the result, a user can undo all changes since each quick fix is entirely revertible due to the command pattern.
+A user might not like a quick fix if it not only fixes an error but also has unintended side effects, such as introducing a different control flow error.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=1\linewidth]{images/quick-fix}
+	\caption{\textit{Quick fixes} in the analysis tool}
+	\label{fig:quick-fixes}
+\end{figure}
 
@@
 
-BPMN analysis tools or formalizations are typically compared by their \textbf{coverage} of BPMN elements~\cite{krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022}.
+BPMN analysis tools or formalizations are typically compared by their \textbf{coverage} of BPMN elements~\cite{krauterHigherorderTransformationApproach2024,krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022,houhouFirstOrderLogicSemantics2019}.
 Our tool already supports the common BPMN elements~\cite{krauterInstantaneousComprehensibleFixable2024}, and we aim for coverage similar to popular BPMN process orchestration platforms such as Camunda.

### 2024-07-05 main.tex
Add benchmark result

@@
 The models repeatedly contain three activities and an exclusive/parallel block with two branches containing one activity per branch (more details in~\cite{krauterInstantaneousComprehensibleFixable2024}).
-The BPMN Analyzer spends from 1 ms up to 9 ms for the BPMN models compared to 0.7 s up to 14 s in our previous tool~\cite{krauterFormalizationAnalysisBPMN2023}.
-In summary, the linear growth of the models leads to a linear growth in state space and, consequently, a linear growth in runtime.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=1\linewidth]{images/model-size-benchmark}
+	\caption{Analysis runtime for models of increasing size}
+	\label{fig:model-size-benchmark}
+\end{figure}
+
+\autoref{fig:model-size-benchmark} shows that the BPMN Analyzer spends from 1 ms up to 9 ms for the BPMN models compared to 0.7 s up to 14 s in our previous tool~\cite{krauterFormalizationAnalysisBPMN2023}.
+In summary, the linear growth of the models leads to a linear growth in state space and, consequently, a linear growth in runtime observed in \autoref{fig:model-size-benchmark}.
 

### 2024-07-05 main.tex
4 pages

@@
 In addition, we demonstrated the instantaneous analysis of the BPMN Analyzer, which outperforms other tools~\cite{krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022} as described in \autoref{sec:innovations}.
-Finally, we have only received positive feedback regarding the tool's usability.
+However, comparing tool performance without standard benchmarks and a reproducible environment remains challenging.
+Finally, we have only received positive feedback regarding the tool's usability, especially the interactive visualization of control flow errors.
+Our visualization builds on the~\cite{camundaservicesgmbhBpmnjsTokenSimulation2024} and is similar to the animation capabilities in~\cite{corradiniFormalisingAnimatingMultiple2022}.
 

### 2024-07-05 main.tex
Enlarge figures

@@
 
-\title{BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Control Flow Analysis for BPMN Models}
+\title{BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Control Flow Analysis for Realistic BPMN Models}
 % TODO: Update the DOI link to fit the extended version on arxiv
@@
 In this paper, we describe a new tool, the \textit{BPMN Analyzer 2.0}\footnote{
-In the following, we will use BPMN Analyzer to refer to the BPMN Analyzer 2.0, not our previous BPMN Analyzer described in~\cite{krauterHigherorderTransformationApproach2024}.}, for analyzing BPMN process models to detect control flow errors \textit{already} during modeling.
+In the following, we will use BPMN Analyzer to refer to the BPMN Analyzer 2.0, not our previous work in~\cite{krauterHigherorderTransformationApproach2024}.}, for analyzing BPMN process models to detect control flow errors \textit{already} during modeling.
 % TODO: Maybe give concrete examples of what we can check!
@@
 
-\begin{figure}[ht]
+\begin{figure*}[ht]
 	\centering
-	\includegraphics[width=1\linewidth]{images/counter-example}
-	\caption{Interactive \textit{erroneous execution} shown in the BPMN Analyzer}
+	\includegraphics[width=0.8\linewidth]{images/counter-example}
+	\caption{\textit{Interactive} erroneous execution example shown in the BPMN Analyzer}
 	\label{fig:counterexample}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}[ht]
+\begin{figure*}[ht]
 	\centering
-	\includegraphics[width=1\linewidth]{images/quick-fix}
-	\caption{\textit{Quick fixes} in the analysis tool}
+	\includegraphics[width=0.8\linewidth]{images/quick-fix}
+	\caption{Suggested \textit{quick fixes} in the BPMN Analyzer}
 	\label{fig:quick-fixes}
-\end{figure}
+\end{figure*}
 

### 2024-07-05 main.tex
Check

@@
 This represents a \textit{worst case} scenario for formal analysis.
-We generated a data set of models~\cite{krauterInstantaneousComprehensibleFixable2024} with a growing number of parallel branches with increasing length, similar to~\cite{corradiniFormalApproachAnalysis2021}.
+We generated a data set of models~\cite{krauterInstantaneousComprehensibleFixable2024} with a growing number of parallel branches with increasing length as shown in \autoref{fig:parallel-branches-models}, similar to~\cite{corradiniFormalApproachAnalysis2021}.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=1\linewidth]{images/parallel-branches}
+	\caption{Models with a growing number of parallel branches and branch length}
+	\label{fig:parallel-branches-models}
+\end{figure}
+
 \autoref{tab:parallel-branches-benchmark} shows the average runtime of our tool when analyzing these models.
@@
 
-% They also want this section
 \section{Maturity of the tool} \label{sec:maturity}
 The BPMN Analyzer is our newest tool, incorporating many findings from our previous work~\cite{krauterFormalizationAnalysisBPMN2023} while focusing on instantaneous and understandable error detection.
-The tool is open-source~\cite{krauterInstantaneousComprehensibleFixable2024}, and we aim to achieve high code quality by employing industry best practices such as rigorous static analysis, testing, and consistent formatting.
-Furthermore, we demonstrated the tool to companies in the BPMN process orchestration space and received positive initial feedback, as described in the introduction.
+The tool is open-source~\cite{krauterInstantaneousComprehensibleFixable2024}, and we aimed for high code quality by employing industry best practices such as rigorous static analysis, testing, and consistent formatting.
+Furthermore, we demonstrated the tool to companies in the BPMN process orchestration space and received positive feedback~\cite{krauterInstantaneousComprehensibleFixable2024}.
 
-% Scalability tests (instantaneous) --> Generated models are public, including our tool for future direct comparisons
 As described in the previous section, we benchmarked our tool runtime in three scenarios.
-The tool can check most models instantaneously, and we provide more details, including scripts and data needed to reproduce our results in~\cite{krauterInstantaneousComprehensibleFixable2024}.
+The tool can check most models instantaneously, and we provide more details, including scripts and all models needed to reproduce our results in~\cite{krauterInstantaneousComprehensibleFixable2024}.
 

### 2024-07-05 main.tex
Related work

@@
 
-BPMN analysis tools or formalizations are typically compared by their \textbf{coverage} of BPMN elements~\cite{krauterHigherorderTransformationApproach2024,krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022,houhouFirstOrderLogicSemantics2019}.
-Our tool already supports the common BPMN elements~\cite{krauterInstantaneousComprehensibleFixable2024}, and we aim for coverage similar to popular BPMN process orchestration platforms such as Camunda.
-% Breakdown of BPMN coverage: https://github.com/timKraeuter/rust_bpmn_analyzer?tab=readme-ov-file#bpmn-coverage
-However, we agree with~\cite{fahlandAnalysisDemandInstantaneous2011} that \textbf{analysis runtime} and \textbf{understandability} are the main issues that hinder the wide adoption of formal analysis tools outside academia.
+\textbf{BPMN specification coverage:}
+Most related work focuses on the depth of BPMN formalization while providing control flow analysis by checking soundness and safeness.
+Thus, these approaches show how different BPMN elements can be formalized and compare themselves with each other regarding supported elements~\cite{corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022,krauterFormalizationAnalysisBPMN2023,krauterHigherorderTransformationApproach2024}.
+The supported BPMN elements come close to the capabilities of popular process orchestration platforms.
+Our tool supports the same depth of BPMN elements as~\cite{corradiniFormalApproachAnalysis2021}, i.e., the most used gateways, tasks, and events.
+A detailed comparison is available in~\cite{timkrauterBPM2024Artifacts2024}, and we plan to support more elements in the future.
+We focus on tool performance and capabilities concerning comprehension, error resolution, and seamless integration into BPMN modeling tools.
 
-Our tool has comparable BPMN element coverage to~\cite{corradiniFormalApproachAnalysis2021} but is still missing some elements when compared to~\cite{krauterFormalizationAnalysisBPMN2023}, which are currently on the roadmap.
-In addition, we demonstrated the instantaneous analysis of the BPMN Analyzer, which outperforms other tools~\cite{krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022} as described in \autoref{sec:innovations}.
-However, comparing tool performance without standard benchmarks and a reproducible environment remains challenging.
-Finally, we have only received positive feedback regarding the tool's usability, especially the interactive visualization of control flow errors.
-Our visualization builds on the~\cite{camundaservicesgmbhBpmnjsTokenSimulation2024} and is similar to the animation capabilities in~\cite{corradiniFormalisingAnimatingMultiple2022}.
+\textbf{Tool performance:}
+Comparing tool performance without standard benchmarks and a reproducible environment is challenging.
+However, other publications indicate that other tools take several seconds up to half a minute to check single soundness properties~\cite{corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022,krauterHigherorderTransformationApproach2024}.
+In contrast, our approach instantaneously checks \textit{all} soundness properties and safeness of the same models.
+The difference in performance lies probably in our pragmatic BPMN encoding optimized for analysis and its direct implementation in an efficient programming language rather than in transforming BPMN into general model-checking tools.
+
+\textbf{Tool capabilities:}
+Another way to compare the different BPMN formalizations and analysis tools is to investigate their capabilities.
+Most tools formalize large parts of the BPMN specification and allow soundness and safeness checking~\cite{corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022,krauterFormalizationAnalysisBPMN2023,krauterHigherorderTransformationApproach2024}.
+Some tools investigate additional aspects such as the introduction of \textit{data} and \textit{time} during verification~\cite{corradiniFormalisingAnimatingMultiple2022,houhouFirstOrderLogicVerification2022}.
+Furthermore, other tools allow specifying and checking \textit{custom temporal logic properties}~\cite{corradiniFormalApproachAnalysis2021,krauterFormalizationAnalysisBPMN2023} and even provide graphical interfaces to ease the specification~\cite{krauterHigherorderTransformationApproach2024}
+Moreover, some tools provide interactive BPMN simulation using token-flow animation~\cite{camundaservicesgmbhBpmnjsTokenSimulation2024,corradiniFormalisingAnimatingMultiple2022}, while others \textit{visualize counterexamples} for soundness violations using tokens~\cite{houhouFirstOrderLogicVerification2022}.
+
+Our tool focuses on \textit{instantaneous} control flow analysis and does not support custom properties, data, or time.
+We do not provide BPMN simulation since other tools already offer this.
+However, we use token-flow animation to visualize control flow errors interactively.
+This improves comprehension compared to previous static, less interactive visualizations.
+In addition, to the best of our knowledge, our tool is the only one that provides \textit{quick fixes}, i.e., automatic resolutions if control flow errors are detected.
+To sum up, our tool incorporates and enhances several ideas from the state of the art while adding novel concepts, such as quick fixes.
+We advocate for a pragmatic approach, prioritizing performance and understanding above all else to ensure seamless integration into BPMN modeling tools.
 

### 2024-07-05 main.tex
Paper more or less done

@@
 Business Process Modeling Notation (BPMN) is becoming increasingly popular for automating processes and orchestrating people and systems.
-However, many process models suffer from control flow errors, such as deadlocks, livelocks, starvation, and lack of synchronization~\cite{fahlandAnalysisDemandInstantaneous2011}.
+However, many process models suffer from control flow errors, such as deadlocks, livelocks, and starvation~\cite{fahlandAnalysisDemandInstantaneous2011}.
 These errors hinder the correct execution of BPMN models and may be detected late in the development process, resulting in elevated costs.
@@
 In the following, we will use BPMN Analyzer to refer to the BPMN Analyzer 2.0, not our previous work in~\cite{krauterHigherorderTransformationApproach2024}.}, for analyzing BPMN process models to detect control flow errors \textit{already} during modeling.
-% TODO: Maybe give concrete examples of what we can check!
 \autoref{fig:overview} shows an overview of the tool.
 The tool front-end is based on the popular \textit{bpmn.io} ecosystem, while the analysis is implemented in Rust for performance and memory efficiency reasons.
+We implemented a breadth-first state space exploration~\cite{clarkeHandbookModelChecking2018}.
+While generating the state space, we check BPMN soundness and safeness~\cite{corradiniClassificationBPMNCollaborations2018} \textit{on-the-fly} to uncover control flow errors.
+Consequently, the tool can detect deadlocks, livelocks, starvation, dead activities, and lack of synchronization in BPMN models.
 The BPMN Analyzer is open-source and accessible online\footnote{\url{https://timkraeuter.com/bpmn-analyzer-js/}} alongside a video demonstration\footnote{\url{https://www.youtube.com/watch?v=MxXbNUl6IjE}}~\cite{krauterInstantaneousComprehensibleFixable2024}.
@@
 
-\textbf{Second}, we benchmarked the tool against a synthetic data set of models that lead to a state space explosion.
+\textbf{Second}, we benchmarked the tool against a synthetic data set of models that lead to a state space explosion~\cite{clarkeHandbookModelChecking2018}.
 This represents a \textit{worst case} scenario for formal analysis.
@@
 Our tool supports the same depth of BPMN elements as~\cite{corradiniFormalApproachAnalysis2021}, i.e., the most used gateways, tasks, and events.
-A detailed comparison is available in~\cite{timkrauterBPM2024Artifacts2024}, and we plan to support more elements in the future.
+A detailed comparison is available in~\cite{krauterInstantaneousComprehensibleFixable2024}, and we plan to support more elements in the future.
 We focus on tool performance and capabilities concerning comprehension, error resolution, and seamless integration into BPMN modeling tools.
@@
 
-\section{Conclusion} \label{sec:conclusion}
+\section{Conclusion \& Future work} \label{sec:conclusion}
 
@@
 We address the three main challenges: \textit{coverage}, \textit{immediacy}, and \textit{consumability} for providing formal analysis to non-expert users as identified in~\cite{fahlandAnalysisDemandInstantaneous2011}.
-In addition, our tool provides quick fixes for common patterns leading to control flow errors.
-One can understand the BPMN Analyzer as a BPMN-specific model checker, implemented in Rust paired with an intuitive user interface based on the popular \textit{bpmn.io} ecosystem that allows easy extension in the future.
+In addition, our tool provides quick fixes for common patterns that lead to control flow errors.
+One can understand the BPMN Analyzer as a BPMN-specific model checker, implemented in Rust paired with an intuitive user interface based on the popular \textit{bpmn.io} ecosystem that is open for extension by design.
+
+In future work, we aim to improve our tool by providing more quick fixes, considering advanced BPMN elements such as different events, and ranking quick fixes based on their usefulness.
+For example, the impact of quick fixes on soundness properties can be part of the ranking since the resulting model can be checked instantaneously in the background.
+Other metrics, such as least change and least surprise from the model repair field, can be used, or one can include previous user behavior.
+Finally, we aspire to test our tool in a real-world scenario to gather feedback and measure its impact on productivity.
 

### 2024-07-05 main.tex
Minor fixes

@@
 Furthermore, we ensure the results are \textit{comprehensible} by highlighting possible violations directly in the model and displaying an interactive counterexample visualization.
-Finally, the tool suggests \textit{fixes} for the most common soundness violations and can be extended to suggest more fixes in the future.
+Finally, the tool suggests \textit{fixes} for the most common control flow errros and can be extended to suggest more fixes in the future.
 
 % Why is it significant for the BPM field?
-Fahland et al.~\cite{fahlandAnalysisDemandInstantaneous2011} describe \textit{coverage}, \textit{immediacy}, and \textit{consumability} as the main challenges for users unaccustomed to formal analysis methods.
+Fahland et al.~\cite{fahlandAnalysisDemandInstantaneous2011} describe \textit{coverage}, \textit{immediacy}, and \textit{consumability} as the main challenges for users unaccustomed to formal analysis.
 The BPMN Analyzer addresses all these challenges since it supports the most common BPMN elements used in practice (coverage), provides \textit{instantaneous} results (immediacy), and a \textit{comprehensible} user interface (consumability), even including suggestions of fixes.
 Developers of industrial BPMN solutions also like our tool, especially the End-2-End user journey~\cite{krauterInstantaneousComprehensibleFixable2024}.
-Thus validating our claim of a UI that is understandable for users unfamiliar with formal analysis methods.
+Thus strengthening our claim of a UI that is understandable to users unfamiliar with formal analysis.
 
@@
 \textbf{First}, we benchmarked how our tool handles \textbf{BPMN models of growing size}.
-We generated 500 synthetic BPMN models starting with five elements up to 4000 elements, increasing linearly in size.
+We generated 500 synthetic BPMN models starting with five elements up to 4000.
 The models repeatedly contain three activities and an exclusive/parallel block with two branches containing one activity per branch (more details in~\cite{krauterInstantaneousComprehensibleFixable2024}).
@@
 However, analysis is still instantaneous for more reasonable models with five parallel branches of length 5 or 3 branches of length 20.
-Other tools report 2-3s of runtime for most soundness properties and 30s for a model with five parallel branches~\cite{corradiniFormalApproachAnalysis2021}, which took us only milliseconds.
+Other tools report 2-3s of runtime for most soundness properties and 30s for a model with five parallel branches~\cite{corradiniFormalApproachAnalysis2021}, which took only milliseconds in our tool.
 
 \textbf{Third}, we applied our tool to eight \textbf{realistic models}, where three models (e001, e002, e020) are taken from~\cite{houhouFirstOrderLogicVerification2022}, and the remaining five models are part of the Camunda BPMN for research repository\footnote{\url{https://github.com/camunda/bpmn-for-research} \label{footnote:camundaResearch}}.
-\autoref{tab:realistic-models-benchmark} shows the average runtime and number of states for each model.
+\autoref{tab:realistic-models-benchmark} shows each model's average runtime and number of states.
 
@@
 In addition to detecting, highlighting, and visualizing control flow errors, the BPMN Analyzer suggests fixes similar to \textit{quick fixes} in Integrated Development Environments.
-Quick fixes cannot be provided for all errors, but we currently cover some patterns leading to deadlocks, lack of synchronization, message starvation, and reused end events.
+Quick fixes cannot be provided for all errors, but we currently cover many patterns leading to deadlocks, lack of synchronization, message starvation, and reused end events.
 The quick fixes we support are described in detail in~\cite{krauterInstantaneousComprehensibleFixable2024} and can be extended independently of the formal analysis.
@@
 Most related work focuses on the depth of BPMN formalization while providing control flow analysis by checking soundness and safeness.
-Thus, these approaches show how different BPMN elements can be formalized and compare themselves with each other regarding supported elements~\cite{corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022,krauterFormalizationAnalysisBPMN2023,krauterHigherorderTransformationApproach2024}.
+Thus, these approaches show how different BPMN elements can be formalized and compare themselves with each other regarding supported elements~\cite{krauterHigherorderTransformationApproach2024,krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022}.
 The supported BPMN elements come close to the capabilities of popular process orchestration platforms.
@@
 Comparing tool performance without standard benchmarks and a reproducible environment is challenging.
-However, other publications indicate that other tools take several seconds up to half a minute to check single soundness properties~\cite{corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022,krauterHigherorderTransformationApproach2024}.
+However, other publications indicate that other tools take several seconds up to half a minute to check single soundness properties~\cite{krauterHigherorderTransformationApproach2024,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022}.
 In contrast, our approach instantaneously checks \textit{all} soundness properties and safeness of the same models.
-The difference in performance lies probably in our pragmatic BPMN encoding optimized for analysis and its direct implementation in an efficient programming language rather than in transforming BPMN into general model-checking tools.
+The difference in performance lies probably in our pragmatic BPMN encoding optimized for analysis and its direct implementation in an efficient programming language rather than using general model-checking tools.
 
@@
 Another way to compare the different BPMN formalizations and analysis tools is to investigate their capabilities.
-Most tools formalize large parts of the BPMN specification and allow soundness and safeness checking~\cite{corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022,krauterFormalizationAnalysisBPMN2023,krauterHigherorderTransformationApproach2024}.
-Some tools investigate additional aspects such as the introduction of \textit{data} and \textit{time} during verification~\cite{corradiniFormalisingAnimatingMultiple2022,houhouFirstOrderLogicVerification2022}.
-Furthermore, other tools allow specifying and checking \textit{custom temporal logic properties}~\cite{corradiniFormalApproachAnalysis2021,krauterFormalizationAnalysisBPMN2023} and even provide graphical interfaces to ease the specification~\cite{krauterHigherorderTransformationApproach2024}
-Moreover, some tools provide interactive BPMN simulation using token-flow animation~\cite{camundaservicesgmbhBpmnjsTokenSimulation2024,corradiniFormalisingAnimatingMultiple2022}, while others \textit{visualize counterexamples} for soundness violations using tokens~\cite{houhouFirstOrderLogicVerification2022}.
+Most tools formalize large parts of the BPMN specification and allow soundness and safeness checking~\cite{krauterHigherorderTransformationApproach2024,krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022}.
+Some tools investigate additional aspects such as the introduction of \textit{data} and \textit{time} during verification~\cite{houhouFirstOrderLogicVerification2022,corradiniFormalisingAnimatingMultiple2022}.
+Furthermore, other tools allow specifying and checking \textit{custom temporal logic properties}~\cite{krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021} and even provide graphical interfaces to ease the specification~\cite{krauterHigherorderTransformationApproach2024}
+Moreover, some tools provide interactive BPMN simulation using token-flow animation~\cite{corradiniFormalisingAnimatingMultiple2022,camundaservicesgmbhBpmnjsTokenSimulation2024}, while others \textit{visualize counterexamples} for soundness violations using tokens~\cite{houhouFirstOrderLogicVerification2022}.
 
@@
 In future work, we aim to improve our tool by providing more quick fixes, considering advanced BPMN elements such as different events, and ranking quick fixes based on their usefulness.
-For example, the impact of quick fixes on soundness properties can be part of the ranking since the resulting model can be checked instantaneously in the background.
-Other metrics, such as least change and least surprise from the model repair field, can be used, or one can include previous user behavior.
+For example, the impact of quick fixes on all control flow errors can be part of the ranking since the resulting model can be checked instantaneously in the background.
+Other metrics, such as least change and least surprise from the model repair field, can be used, or one can learn from previous user behavior.
 Finally, we aspire to test our tool in a real-world scenario to gather feedback and measure its impact on productivity.

### 2024-07-05 main.tex
Update youtube link

@@
 Consequently, the tool can detect deadlocks, livelocks, starvation, dead activities, and lack of synchronization in BPMN models.
-The BPMN Analyzer is open-source and accessible online\footnote{\url{https://timkraeuter.com/bpmn-analyzer-js/}} alongside a video demonstration\footnote{\url{https://www.youtube.com/watch?v=MxXbNUl6IjE}}~\cite{krauterInstantaneousComprehensibleFixable2024}.
+The BPMN Analyzer is open-source and accessible online\footnote{\url{https://timkraeuter.com/bpmn-analyzer-js/}} alongside a video demonstration\footnote{\url{https://www.youtube.com/watch?v=Nv2W-hXNZYA}}~\cite{krauterInstantaneousComprehensibleFixable2024}.
 

### 2024-07-09 main.tex
Cleanup
Typos and language

@@
 \documentclass[
-twocolumn
+twocolumn,
 % hf, % <-- Not sure if this should be enabled
@@
 \title{BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Control Flow Analysis for Realistic BPMN Models}
-% TODO: Update the DOI link to fit the extended version on arxiv
 
@@
 Moreover, the tool directly displays detected errors in the model, including an interactive visualization, and suggests fixes to resolve them.
-The tool is open-source, extensible, and integrated into a popular BPMN modeling tool.
+The tool is open source, extensible, and integrated into a popular BPMN modeling tool.
 \end{abstract}
@@
 \maketitle
-% 5 pages including references
 
@@
 We implemented a breadth-first state space exploration~\cite{clarkeHandbookModelChecking2018}.
-While generating the state space, we check BPMN soundness and safeness~\cite{corradiniClassificationBPMNCollaborations2018} \textit{on-the-fly} to uncover control flow errors.
+While generating the state space, we check BPMN soundness and safeness~\cite{corradiniClassificationBPMNCollaborations2018} \textit{on the fly} to uncover control flow errors.
 Consequently, the tool can detect deadlocks, livelocks, starvation, dead activities, and lack of synchronization in BPMN models.
-The BPMN Analyzer is open-source and accessible online\footnote{\url{https://timkraeuter.com/bpmn-analyzer-js/}} alongside a video demonstration\footnote{\url{https://www.youtube.com/watch?v=Nv2W-hXNZYA}}~\cite{krauterInstantaneousComprehensibleFixable2024}.
+The BPMN Analyzer is open source and accessible online\footnote{\url{https://timkraeuter.com/bpmn-analyzer-js/}} alongside a video demonstration\footnote{\url{https://www.youtube.com/watch?v=Nv2W-hXNZYA}}~\cite{krauterInstantaneousComprehensibleFixable2024}.
 
@@
 Furthermore, we ensure the results are \textit{comprehensible} by highlighting possible violations directly in the model and displaying an interactive counterexample visualization.
-Finally, the tool suggests \textit{fixes} for the most common control flow errros and can be extended to suggest more fixes in the future.
+Finally, the tool suggests \textit{fixes} for the most common control flow errors and can be extended to suggest more fixes in the future.
 
@@
 Fahland et al.~\cite{fahlandAnalysisDemandInstantaneous2011} describe \textit{coverage}, \textit{immediacy}, and \textit{consumability} as the main challenges for users unaccustomed to formal analysis.
-The BPMN Analyzer addresses all these challenges since it supports the most common BPMN elements used in practice (coverage), provides \textit{instantaneous} results (immediacy), and a \textit{comprehensible} user interface (consumability), even including suggestions of fixes.
-Developers of industrial BPMN solutions also like our tool, especially the End-2-End user journey~\cite{krauterInstantaneousComprehensibleFixable2024}.
-Thus strengthening our claim of a UI that is understandable to users unfamiliar with formal analysis.
+The BPMN Analyzer addresses all these challenges since it supports the most common BPMN elements used in practice (coverage), provides \textit{instantaneous} results (immediacy), and a \textit{comprehensible} user interface (consumability), even including suggestions for fixes.
+Developers of industrial BPMN solutions also like our tool, especially the End-to-end user journey~\cite{krauterInstantaneousComprehensibleFixable2024}.
+Thus, this strengthens our claim of a UI that is understandable to users unfamiliar with formal analysis.
 
@@
 
-We demonstrate instantaneous control flow analysis by benchmarking our tool in \textit{three} different scenarios.
+We demonstrate instantaneous control flow analysis by benchmarking our tool in \textit{three} scenarios.
 For all our benchmarks, we use the hyperfine benchmarking tool \cite{peterHyperfine2023} (version 1.18.0), which calculates the average runtime when executing each control flow analysis ten or more times.
-The benchmarks were run on Ubuntu 22.04.4 with an AMD Ryzen 7700X processor (4.5GHz) and 32 GB of RAM (5600 MHz).
+We ran the benchmarks on Ubuntu 22.04.4 with an AMD Ryzen 7700X processor (4.5GHz) and 32 GB of RAM (5600 MHz).
 All used BPMN models, our tools to generate them, and benchmarking scripts to run them are available in~\cite{krauterInstantaneousComprehensibleFixable2024}.
@@
 
-\textbf{Second}, we benchmarked the tool against a synthetic data set of models that lead to a state space explosion~\cite{clarkeHandbookModelChecking2018}.
-This represents a \textit{worst case} scenario for formal analysis.
-We generated a data set of models~\cite{krauterInstantaneousComprehensibleFixable2024} with a growing number of parallel branches with increasing length as shown in \autoref{fig:parallel-branches-models}, similar to~\cite{corradiniFormalApproachAnalysis2021}.
+\textbf{Second}, we benchmarked the tool against a synthetic data set of models that led to a state space explosion~\cite{clarkeHandbookModelChecking2018}.
+This represents a \textit{worst-case} scenario for formal analysis.
+We generated a data set of models~\cite{krauterInstantaneousComprehensibleFixable2024} with a growing number of parallel branches with increasing length, as shown in \autoref{fig:parallel-branches-models}, like~\cite{corradiniFormalApproachAnalysis2021}.
 
@@
 
-The BPMN Analyzer takes 1-10ms for e001, e002, and e020 ~\cite{krauterInstantaneousComprehensibleFixable2024} while~\cite{houhouFirstOrderLogicVerification2022} and~\cite{krauterFormalizationAnalysisBPMN2023} report 3.66-10.26s and 1-1.75s.
+The BPMN Analyzer takes 1-10ms for e001, e002, and e020~\cite{krauterInstantaneousComprehensibleFixable2024}, while~\cite{houhouFirstOrderLogicVerification2022} and~\cite{krauterFormalizationAnalysisBPMN2023} report 3.66-10.26s and 1-1.75s respectively.
 The benchmarks in~\cite{krauterFormalizationAnalysisBPMN2023} were run on the same hardware, while the machine used in~\cite{houhouFirstOrderLogicVerification2022} was slightly less powerful.
-To summarize, we believe our analysis is instantaneous for nearly all models since most models have relatively small state spaces (less than 1000 states, see~\cite{fahlandAnalysisDemandInstantaneous2011}).
+To summarize, our analysis is instantaneous for nearly all models since most models have relatively small state spaces (less than 1000 states, see~\cite{fahlandAnalysisDemandInstantaneous2011}).
 
@@
 % Counterexample
-\textbf{Second}, we use \textit{tokens} to \textit{interactively} visualize errors, i.e., we show an execution leading to the error.
+\textbf{Second}, we use \textit{tokens} to visualize errors \textit{interactively}, i.e., show an execution leading to the error.
 Our analysis provides sample executions leading to the possible control-flow errors, which we visualize directly in the BPMN editor by showing how tokens move from the process start to an erroneous state.
@@
 In \autoref{fig:counterexample}, the visualization has been \textit{paused} just before an \textit{unsafe} state was reached.
-One token is already located at the sequence flow, which is marked, while a second token is currently waiting at the exclusive gateway \textsf{e1}.
+One token is already located at the marked sequence flow, while a second token is currently waiting at the exclusive gateway \textsf{e1}.
 The visualization can be resumed or restarted using the play and restart button on the left side.
-When resumed, the gateway \textsf{e1} will execute, resulting in two tokens at the subsequent sequence flow, i.e., an unsafe execution state.
+The gateway \textsf{e1} will execute when resumed, resulting in two tokens at the subsequent sequence flow, i.e., an unsafe execution state.
 In addition, one can control the visualization speed using the bottom buttons next to the speedometer.
@@
 \subsection{Fixable Analysis}
-In addition to detecting, highlighting, and visualizing control flow errors, the BPMN Analyzer suggests fixes similar to \textit{quick fixes} in Integrated Development Environments.
+In addition to detecting, highlighting, and visualizing control flow errors, the BPMN Analyzer suggests fixes like \textit{quick fixes} in Integrated Development Environments.
 Quick fixes cannot be provided for all errors, but we currently cover many patterns leading to deadlocks, lack of synchronization, message starvation, and reused end events.
@@
 
-\section{Maturity of the tool} \label{sec:maturity}
+\section{Maturity of the Tool} \label{sec:maturity}
 The BPMN Analyzer is our newest tool, incorporating many findings from our previous work~\cite{krauterFormalizationAnalysisBPMN2023} while focusing on instantaneous and understandable error detection.
-The tool is open-source~\cite{krauterInstantaneousComprehensibleFixable2024}, and we aimed for high code quality by employing industry best practices such as rigorous static analysis, testing, and consistent formatting.
+The tool is open source~\cite{krauterInstantaneousComprehensibleFixable2024}, and we aimed to achieve high code quality by employing industry best practices such as rigorous static analysis, testing, and consistent formatting.
 Furthermore, we demonstrated the tool to companies in the BPMN process orchestration space and received positive feedback~\cite{krauterInstantaneousComprehensibleFixable2024}.
@@
 As described in the previous section, we benchmarked our tool runtime in three scenarios.
-The tool can check most models instantaneously, and we provide more details, including scripts and all models needed to reproduce our results in~\cite{krauterInstantaneousComprehensibleFixable2024}.
+The tool can check most models instantaneously, and we provide all details, including scripts and all models needed to reproduce our results~\cite{krauterInstantaneousComprehensibleFixable2024}.
 
-\section{Related work} \label{sec:related-work}
+\section{Related Work} \label{sec:related-work}
 
@@
 Most related work focuses on the depth of BPMN formalization while providing control flow analysis by checking soundness and safeness.
-Thus, these approaches show how different BPMN elements can be formalized and compare themselves with each other regarding supported elements~\cite{krauterHigherorderTransformationApproach2024,krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022}.
+Thus, these approaches show how different BPMN elements can be formalized and compared regarding supported elements~\cite{krauterHigherorderTransformationApproach2024,krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022}.
 The supported BPMN elements come close to the capabilities of popular process orchestration platforms.
@@
 In contrast, our approach instantaneously checks \textit{all} soundness properties and safeness of the same models.
-The difference in performance lies probably in our pragmatic BPMN encoding optimized for analysis and its direct implementation in an efficient programming language rather than using general model-checking tools.
+The difference in performance lies in our pragmatic BPMN encoding optimized for analysis and its direct implementation in an efficient programming language rather than using general model-checking tools.
 
@@
 Most tools formalize large parts of the BPMN specification and allow soundness and safeness checking~\cite{krauterHigherorderTransformationApproach2024,krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022}.
-Some tools investigate additional aspects such as the introduction of \textit{data} and \textit{time} during verification~\cite{houhouFirstOrderLogicVerification2022,corradiniFormalisingAnimatingMultiple2022}.
-Furthermore, other tools allow specifying and checking \textit{custom temporal logic properties}~\cite{krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021} and even provide graphical interfaces to ease the specification~\cite{krauterHigherorderTransformationApproach2024}
+Some tools investigate additional aspects, such as the introduction of \textit{data} and \textit{time} during verification~\cite{houhouFirstOrderLogicVerification2022,corradiniFormalisingAnimatingMultiple2022}.
+Furthermore, other tools allow specifying and checking \textit{custom temporal logic properties}~\cite{krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021} and even provide graphical interfaces to ease the specification~\cite{krauterHigherorderTransformationApproach2024}.
 Moreover, some tools provide interactive BPMN simulation using token-flow animation~\cite{corradiniFormalisingAnimatingMultiple2022,camundaservicesgmbhBpmnjsTokenSimulation2024}, while others \textit{visualize counterexamples} for soundness violations using tokens~\cite{houhouFirstOrderLogicVerification2022}.
@@
 
-\section{Conclusion \& Future work} \label{sec:conclusion}
+\section{Conclusion \& Future Work} \label{sec:conclusion}
 
@@
 We benchmarked our tool against synthetic and realistic BPMN models to demonstrate instantaneous soundness checking.
-We address the three main challenges: \textit{coverage}, \textit{immediacy}, and \textit{consumability} for providing formal analysis to non-expert users as identified in~\cite{fahlandAnalysisDemandInstantaneous2011}.
-In addition, our tool provides quick fixes for common patterns that lead to control flow errors.
+We address the three main challenges, \textit{coverage}, \textit{immediacy}, and \textit{consumability}, to provide formal analysis to non-expert users as identified in~\cite{fahlandAnalysisDemandInstantaneous2011}.
+In addition, our tool offers quick fixes for common patterns that lead to control flow errors.
 One can understand the BPMN Analyzer as a BPMN-specific model checker, implemented in Rust paired with an intuitive user interface based on the popular \textit{bpmn.io} ecosystem that is open for extension by design.

### 2024-07-31 main.tex
Layout
Update metadata

@@
 \documentclass[
-twocolumn,
+twocolumn, % TODO: has to be one col
 % hf, % <-- Not sure if this should be enabled
@@
 
-\conference{BPM 2024: Demos and Resources, September 01-06, 2024, Krakow, PL}
+\conference{Proceedings of the Best BPM Dissertation Award, Doctoral Consortium, and Demonstrations \& Resources Forum co-located with 22nd International Conference on Business Process Management (BPM 2024), Krakow, Poland, September 1st to 6th, 2024.}
 
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{images/counter-example}
+	\includegraphics[width=0.82\linewidth]{images/counter-example}
 	\caption{\textit{Interactive} erroneous execution example shown in the BPMN Analyzer}
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{images/quick-fix}
+	\includegraphics[width=0.82\linewidth]{images/quick-fix}
 	\caption{Suggested \textit{quick fixes} in the BPMN Analyzer}

### 2024-07-31 main.tex
Reduce paper size

@@
 \documentclass[
-twocolumn, % TODO: has to be one col
+onecolumn, % TODO: has to be one col
 % hf, % <-- Not sure if this should be enabled
@@
 We generated 500 synthetic BPMN models starting with five elements up to 4000.
-The models repeatedly contain three activities and an exclusive/parallel block with two branches containing one activity per branch (more details in~\cite{krauterInstantaneousComprehensibleFixable2024}).
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=1\linewidth]{images/model-size-benchmark}
-	\caption{Analysis runtime for models of increasing size}
-	\label{fig:model-size-benchmark}
-\end{figure}
-
-\autoref{fig:model-size-benchmark} shows that the BPMN Analyzer spends from 1 ms up to 9 ms for the BPMN models compared to 0.7 s up to 14 s in our previous tool~\cite{krauterFormalizationAnalysisBPMN2023}.
-In summary, the linear growth of the models leads to a linear growth in state space and, consequently, a linear growth in runtime observed in \autoref{fig:model-size-benchmark}.
+The models repeatedly contain three activities and an exclusive/parallel block with two branches containing one activity per branch (see ~\cite{krauterInstantaneousComprehensibleFixable2024}).
+The BPMN Analyzer spends from 1 ms up to 9 ms for the BPMN models~\cite{krauterInstantaneousComprehensibleFixable2024} compared to 0.7 s up to 14 s in our previous tool~\cite{krauterFormalizationAnalysisBPMN2023}.
+In summary, the linear growth of the models leads to a linear growth in state space and, consequently, a linear growth in runtime.
 
@@
 	\centering
-	\includegraphics[width=1\linewidth]{images/parallel-branches}
+	\includegraphics[width=0.5\linewidth]{images/parallel-branches}
 	\caption{Models with a growing number of parallel branches and branch length}
@@
 
-\begin{figure*}[ht]
+\begin{figure}[ht]
 	\centering
-	\includegraphics[width=0.82\linewidth]{images/counter-example}
+	\includegraphics[width=0.6\linewidth]{images/counter-example}
 	\caption{\textit{Interactive} erroneous execution example shown in the BPMN Analyzer}
 	\label{fig:counterexample}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}[ht]
+\begin{figure}[ht]
 	\centering
-	\includegraphics[width=0.82\linewidth]{images/quick-fix}
+	\includegraphics[width=0.6\linewidth]{images/quick-fix}
 	\caption{Suggested \textit{quick fixes} in the BPMN Analyzer}
 	\label{fig:quick-fixes}
-\end{figure*}
+\end{figure}
 

### 2024-07-31 main.tex
Merge tables
Save space

@@
 	\centering
-	\includegraphics[width=1\linewidth]{images/overview}
+	\includegraphics[width=0.5\linewidth]{images/overview}
 	\caption{Overview of the BPMN Analyzer 2.0}
@@
 The BPMN Analyzer explores the entire state space while simultaneously analyzing the control flow, i.e., verifying soundness properties.
+The models' state space grows exponentially, leading to the same order of growth in runtime.
+Our analysis is not instantaneous anymore when approaching 17 parallel branches of length 1 (see \autoref{tab:parallel-branches-benchmark}).
+However, analysis is still instantaneous for more reasonable models with five parallel branches of length 5 or 3 branches of length 20.
+Other tools report 2-3s of runtime for most soundness properties and 30s for a model with five parallel branches~\cite{corradiniFormalApproachAnalysis2021}, which took milliseconds in our tool.
 
-\begin{table}[h]
+\begin{table}[ht]
+    \begin{minipage}{.51\linewidth}
 	   \centering
@@
 	   		hline{1, 2, Z} = {-}{1.2pt, solid}, % Z is the last row/column
-			hline{8, 10} = {-}{dashed},
+	   		hline{8, 9} = {-}{dashed},
 	   		vline{2-Y} = {2-Z}{solid}, % Y is the second to last row/column
@@
 	       20 & 1 & 8.803 ms& 1.048.579 \\
-		5 & 3 & 3 ms& 1.027 \\
 	       5 & 5 & 14 ms& 7.779 \\
-		3 & 10 & 2 ms& 1.334 \\
 	       3 & 20 & 11 ms& 9.264 \\
 	   \end{tblr}
-\end{table}
-
-The models' state space grows exponentially, leading to the same order of growth in runtime.
-Our analysis is not instantaneous anymore when approaching 17 parallel branches of length 1 (see \autoref{tab:parallel-branches-benchmark}).
-However, analysis is still instantaneous for more reasonable models with five parallel branches of length 5 or 3 branches of length 20.
-Other tools report 2-3s of runtime for most soundness properties and 30s for a model with five parallel branches~\cite{corradiniFormalApproachAnalysis2021}, which took only milliseconds in our tool.
-
-\textbf{Third}, we applied our tool to eight \textbf{realistic models}, where three models (e001, e002, e020) are taken from~\cite{houhouFirstOrderLogicVerification2022}, and the remaining five models are part of the Camunda BPMN for research repository\footnote{\url{https://github.com/camunda/bpmn-for-research} \label{footnote:camundaResearch}}.
-\autoref{tab:realistic-models-benchmark} shows each model's average runtime and number of states.
-
-\begin{table}[h]
+    \end{minipage}%
+    \begin{minipage}{.5\linewidth}
 	   \centering
@@
 	   \end{tblr}
+    \end{minipage} 
 \end{table}
 
+\textbf{Third}, we applied our tool to eight \textbf{realistic models}, where three models (e001, e002, e020) are taken from~\cite{houhouFirstOrderLogicVerification2022}, and the remaining five models are part of the Camunda BPMN for research repository\footnote{\url{https://github.com/camunda/bpmn-for-research} \label{footnote:camundaResearch}}.
+\autoref{tab:realistic-models-benchmark} shows each model's average runtime and number of states.
 The BPMN Analyzer takes 1-10ms for e001, e002, and e020~\cite{krauterInstantaneousComprehensibleFixable2024}, while~\cite{houhouFirstOrderLogicVerification2022} and~\cite{krauterFormalizationAnalysisBPMN2023} report 3.66-10.26s and 1-1.75s respectively.

### 2024-07-31 main.tex
Shorten references

@@
 We demonstrate instantaneous control flow analysis by benchmarking our tool in \textit{three} scenarios.
-For all our benchmarks, we use the hyperfine benchmarking tool \cite{peterHyperfine2023} (version 1.18.0), which calculates the average runtime when executing each control flow analysis ten or more times.
+For all our benchmarks, we use the hyperfine benchmarking tool (version 1.18.0), which calculates the average runtime when executing each control flow analysis ten or more times.
 We ran the benchmarks on Ubuntu 22.04.4 with an AMD Ryzen 7700X processor (4.5GHz) and 32 GB of RAM (5600 MHz).
@@
 The models repeatedly contain three activities and an exclusive/parallel block with two branches containing one activity per branch (see ~\cite{krauterInstantaneousComprehensibleFixable2024}).
-The BPMN Analyzer spends from 1 ms up to 9 ms for the BPMN models~\cite{krauterInstantaneousComprehensibleFixable2024} compared to 0.7 s up to 14 s in our previous tool~\cite{krauterFormalizationAnalysisBPMN2023}.
+The BPMN Analyzer spends from 1 ms up to 9 ms for the BPMN models~\cite{krauterInstantaneousComprehensibleFixable2024} compared to 0.7 s up to 14 s in our previous tool~\cite{krauterHigherorderTransformationApproach2024}.
 In summary, the linear growth of the models leads to a linear growth in state space and, consequently, a linear growth in runtime.
@@
 \begin{table}[ht]
+% \scalebox{0.8}{ % TODO: Not sure about scalebox yet.
     \begin{minipage}{.51\linewidth}
@@
     \end{minipage}%
+    \qquad
     \begin{minipage}{.5\linewidth}
@@
     \end{minipage} 
+% }
 \end{table}
@@
 \autoref{tab:realistic-models-benchmark} shows each model's average runtime and number of states.
-The BPMN Analyzer takes 1-10ms for e001, e002, and e020~\cite{krauterInstantaneousComprehensibleFixable2024}, while~\cite{houhouFirstOrderLogicVerification2022} and~\cite{krauterFormalizationAnalysisBPMN2023} report 3.66-10.26s and 1-1.75s respectively.
-The benchmarks in~\cite{krauterFormalizationAnalysisBPMN2023} were run on the same hardware, while the machine used in~\cite{houhouFirstOrderLogicVerification2022} was slightly less powerful.
+The BPMN Analyzer takes 1-10ms for e001, e002, and e020~\cite{krauterInstantaneousComprehensibleFixable2024}, while~\cite{houhouFirstOrderLogicVerification2022} and~\cite{krauterHigherorderTransformationApproach2024} report 3.66-10.26s and 1-1.75s respectively.
+The benchmarks in~\cite{krauterHigherorderTransformationApproach2024} were run on the same hardware, while the machine used in~\cite{houhouFirstOrderLogicVerification2022} was slightly less powerful.
 To summarize, our analysis is instantaneous for nearly all models since most models have relatively small state spaces (less than 1000 states, see~\cite{fahlandAnalysisDemandInstantaneous2011}).
@@
 \section{Maturity of the Tool} \label{sec:maturity}
-The BPMN Analyzer is our newest tool, incorporating many findings from our previous work~\cite{krauterFormalizationAnalysisBPMN2023} while focusing on instantaneous and understandable error detection.
+The BPMN Analyzer is our newest tool, incorporating many findings from our previous work~\cite{krauterHigherorderTransformationApproach2024} while focusing on instantaneous and understandable error detection.
 The tool is open source~\cite{krauterInstantaneousComprehensibleFixable2024}, and we aimed to achieve high code quality by employing industry best practices such as rigorous static analysis, testing, and consistent formatting.
@@
 Most related work focuses on the depth of BPMN formalization while providing control flow analysis by checking soundness and safeness.
-Thus, these approaches show how different BPMN elements can be formalized and compared regarding supported elements~\cite{krauterHigherorderTransformationApproach2024,krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022}.
+Thus, these approaches show how different BPMN elements can be formalized and compared regarding supported elements~\cite{krauterHigherorderTransformationApproach2024,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022}.
 The supported BPMN elements come close to the capabilities of popular process orchestration platforms.
@@
 Another way to compare the different BPMN formalizations and analysis tools is to investigate their capabilities.
-Most tools formalize large parts of the BPMN specification and allow soundness and safeness checking~\cite{krauterHigherorderTransformationApproach2024,krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022}.
+Most tools formalize large parts of the BPMN specification and allow soundness and safeness checking~\cite{krauterHigherorderTransformationApproach2024,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022}.
 Some tools investigate additional aspects, such as the introduction of \textit{data} and \textit{time} during verification~\cite{houhouFirstOrderLogicVerification2022,corradiniFormalisingAnimatingMultiple2022}.
-Furthermore, other tools allow specifying and checking \textit{custom temporal logic properties}~\cite{krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021} and even provide graphical interfaces to ease the specification~\cite{krauterHigherorderTransformationApproach2024}.
+Furthermore, other tools allow specifying and checking \textit{custom temporal logic properties}~\cite{krauterHigherorderTransformationApproach2024,corradiniFormalApproachAnalysis2021} and even provide graphical interfaces to ease the specification~\cite{krauterHigherorderTransformationApproach2024}.
 Moreover, some tools provide interactive BPMN simulation using token-flow animation~\cite{corradiniFormalisingAnimatingMultiple2022,camundaservicesgmbhBpmnjsTokenSimulation2024}, while others \textit{visualize counterexamples} for soundness violations using tokens~\cite{houhouFirstOrderLogicVerification2022}.

### 2024-07-31 main.tex
Cleanup citations

@@
     \end{minipage}%
-    \qquad
     \begin{minipage}{.5\linewidth}
@@
 Furthermore, other tools allow specifying and checking \textit{custom temporal logic properties}~\cite{krauterHigherorderTransformationApproach2024,corradiniFormalApproachAnalysis2021} and even provide graphical interfaces to ease the specification~\cite{krauterHigherorderTransformationApproach2024}.
-Moreover, some tools provide interactive BPMN simulation using token-flow animation~\cite{corradiniFormalisingAnimatingMultiple2022,camundaservicesgmbhBpmnjsTokenSimulation2024}, while others \textit{visualize counterexamples} for soundness violations using tokens~\cite{houhouFirstOrderLogicVerification2022}.
+Moreover, some tools provide interactive BPMN simulation using token-flow animation~\cite{corradiniFormalisingAnimatingMultiple2022}, while others \textit{visualize counterexamples} for soundness violations using tokens~\cite{houhouFirstOrderLogicVerification2022}.
 

### 2024-07-31 main.tex
Space optimizations

@@
 The tool front-end is based on the popular \textit{bpmn.io} ecosystem, while the analysis is implemented in Rust for performance and memory efficiency reasons.
-We implemented a breadth-first state space exploration~\cite{clarkeHandbookModelChecking2018}.
+We implemented a breadth-first state space exploration.
 While generating the state space, we check BPMN soundness and safeness~\cite{corradiniClassificationBPMNCollaborations2018} \textit{on the fly} to uncover control flow errors.
@@
 
-\textbf{Second}, we benchmarked the tool against a synthetic data set of models that led to a state space explosion~\cite{clarkeHandbookModelChecking2018}.
+\textbf{Second}, we benchmarked the tool against a synthetic data set of models that led to a state space explosion.
 This represents a \textit{worst-case} scenario for formal analysis.
@@
 % Describe the figure.
-In \autoref{fig:counterexample}, the visualization has been \textit{paused} just before an \textit{unsafe} state was reached.
+In \autoref{fig:screenshots}, the visualization has been \textit{paused} just before an \textit{unsafe} state was reached.
 One token is already located at the marked sequence flow, while a second token is currently waiting at the exclusive gateway \textsf{e1}.
@@
 In addition, one can control the visualization speed using the bottom buttons next to the speedometer.
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=0.6\linewidth]{images/counter-example}
-	\caption{\textit{Interactive} erroneous execution example shown in the BPMN Analyzer}
-	\label{fig:counterexample}
-\end{figure}
 
@@
 
-For example, \autoref{fig:quick-fixes} shows a screenshot of our tool, where quick fixes are depicted as green overlays containing a light bulb icon.
+For example, \autoref{fig:screenshots} shows a screenshot of our tool, where quick fixes are depicted as green overlays containing a light bulb icon.
 A user can apply a quick fix by clicking on a green overlay and instantly see the changes regarding control flow errors.
@@
 	\centering
-	\includegraphics[width=0.6\linewidth]{images/quick-fix}
-	\caption{Suggested \textit{quick fixes} in the BPMN Analyzer}
-	\label{fig:quick-fixes}
+	\includegraphics[width=0.8\linewidth]{images/tool-screenshots}
+	\caption{Execution visualization (left) and suggested \textit{quick fixes} (right) in the BPMN Analyzer}
+	\label{fig:screenshots}
 \end{figure}
@@
 \section{Maturity of the Tool} \label{sec:maturity}
-The BPMN Analyzer is our newest tool, incorporating many findings from our previous work~\cite{krauterHigherorderTransformationApproach2024} while focusing on instantaneous and understandable error detection.
+The BPMN Analyzer is our newest tool, incorporating many findings from our previous work~\cite{krauterHigherorderTransformationApproach2024} while focusing on instantaneous and understandable error detectionn, as described in the previous section.
 The tool is open source~\cite{krauterInstantaneousComprehensibleFixable2024}, and we aimed to achieve high code quality by employing industry best practices such as rigorous static analysis, testing, and consistent formatting.
 Furthermore, we demonstrated the tool to companies in the BPMN process orchestration space and received positive feedback~\cite{krauterInstantaneousComprehensibleFixable2024}.
-
-As described in the previous section, we benchmarked our tool runtime in three scenarios.
-The tool can check most models instantaneously, and we provide all details, including scripts and all models needed to reproduce our results~\cite{krauterInstantaneousComprehensibleFixable2024}.
 
@@
 
-In future work, we aim to improve our tool by providing more quick fixes, considering advanced BPMN elements such as different events, and ranking quick fixes based on their usefulness.
-For example, the impact of quick fixes on all control flow errors can be part of the ranking since the resulting model can be checked instantaneously in the background.
-Other metrics, such as least change and least surprise from the model repair field, can be used, or one can learn from previous user behavior.
+In future work, we aim to improve our tool by providing more quick fixes, considering advanced BPMN elements such as different events, and ranking quick fixes based on usefulness and previous user behavior.
 Finally, we aspire to test our tool in a real-world scenario to gather feedback and measure its impact on productivity.
-
-% \begin{acknowledgments}
-% Thanks to the anonymous reviewers for their valuable feedback.
-% \end{acknowledgments}
 

### 2024-07-31 paper.tex
Merge related work and maturity

--- 2024-07-31 main.tex
@@
 In the remainder of the paper, we describe how instantaneous, comprehensible, and fixable control flow error detection is achieved in \autoref{sec:innovations}.
-Then, we discuss the maturity of our tool in \autoref{sec:maturity} before presenting related work in \autoref{sec:related-work}.
-Finally, we conclude in \autoref{sec:conclusion}.
+Then, we discuss related work and tool maturity in \autoref{sec:related-work} before concluding in \autoref{sec:conclusion}.
 
@@
 
-\section{Maturity of the Tool} \label{sec:maturity}
-The BPMN Analyzer is our newest tool, incorporating many findings from our previous work~\cite{krauterHigherorderTransformationApproach2024} while focusing on instantaneous and understandable error detectionn, as described in the previous section.
-The tool is open source~\cite{krauterInstantaneousComprehensibleFixable2024}, and we aimed to achieve high code quality by employing industry best practices such as rigorous static analysis, testing, and consistent formatting.
-Furthermore, we demonstrated the tool to companies in the BPMN process orchestration space and received positive feedback~\cite{krauterInstantaneousComprehensibleFixable2024}.
-
-\section{Related Work} \label{sec:related-work}
+\section{Related Work \& Maturity of the Tool} \label{sec:related-work}
 
@@
 
-Our tool focuses on \textit{instantaneous} control flow analysis and does not support custom properties, data, or time.
-We do not provide BPMN simulation since other tools already offer this.
-However, we use token-flow animation to visualize control flow errors interactively.
-This improves comprehension compared to previous static, less interactive visualizations.
-In addition, to the best of our knowledge, our tool is the only one that provides \textit{quick fixes}, i.e., automatic resolutions if control flow errors are detected.
-To sum up, our tool incorporates and enhances several ideas from the state of the art while adding novel concepts, such as quick fixes.
+The BPMN Analyzer is our newest tool, which incorporates and enhances several ideas from the state of the art and focuses on instantaneous control flow analysis.
+The tool is open source~\cite{krauterInstantaneousComprehensibleFixable2024}, and we aimed to achieve high code quality by employing industry best practices such as rigorous static analysis, testing, and consistent formatting.
+Furthermore, we received positive feedbacked from companies in the BPMN process orchestration space~\cite{krauterInstantaneousComprehensibleFixable2024}.
+We use token-flow animation to visualize control flow errors interactively, which improves comprehension compared to previous, non-interactive visualizations.
+In addition, to the best of our knowledge, the tool is the only one that provides \textit{quick fixes}, i.e., automatic resolutions if control flow errors are detected.
 We advocate for a pragmatic approach, prioritizing performance and understanding above all else to ensure seamless integration into BPMN modeling tools.

### 2024-08-01 paper.tex
Remove related work

--- 2024-07-31 main.tex
@@
 The BPMN Analyzer addresses all these challenges since it supports the most common BPMN elements used in practice (coverage), provides \textit{instantaneous} results (immediacy), and a \textit{comprehensible} user interface (consumability), even including suggestions for fixes.
-Developers of industrial BPMN solutions also like our tool, especially the End-to-end user journey~\cite{krauterInstantaneousComprehensibleFixable2024}.
-Thus, this strengthens our claim of a UI that is understandable to users unfamiliar with formal analysis.
+Developers of industrial BPMN software also like our tool, especially the End-to-end user journey~\cite{krauterInstantaneousComprehensibleFixable2024}.
+Thus, this supports our claim that the UI is easy for users unfamiliar with formal analysis to understand.
 
@@
 In the remainder of the paper, we describe how instantaneous, comprehensible, and fixable control flow error detection is achieved in \autoref{sec:innovations}.
-Then, we discuss the maturity of our tool in \autoref{sec:maturity} before presenting related work in \autoref{sec:related-work}.
-Finally, we conclude in \autoref{sec:conclusion}.
+Then, we discuss tool maturity in \autoref{sec:maturity} before concluding in \autoref{sec:conclusion}.
 
@@
 
-\section{Related Work} \label{sec:related-work}
-
-\textbf{BPMN specification coverage:}
-Most related work focuses on the depth of BPMN formalization while providing control flow analysis by checking soundness and safeness.
-Thus, these approaches show how different BPMN elements can be formalized and compared regarding supported elements~\cite{krauterHigherorderTransformationApproach2024,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022}.
-The supported BPMN elements come close to the capabilities of popular process orchestration platforms.
-Our tool supports the same depth of BPMN elements as~\cite{corradiniFormalApproachAnalysis2021}, i.e., the most used gateways, tasks, and events.
-A detailed comparison is available in~\cite{krauterInstantaneousComprehensibleFixable2024}, and we plan to support more elements in the future.
-We focus on tool performance and capabilities concerning comprehension, error resolution, and seamless integration into BPMN modeling tools.
-
-\textbf{Tool performance:}
-Comparing tool performance without standard benchmarks and a reproducible environment is challenging.
-However, other publications indicate that other tools take several seconds up to half a minute to check single soundness properties~\cite{krauterHigherorderTransformationApproach2024,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022}.
-In contrast, our approach instantaneously checks \textit{all} soundness properties and safeness of the same models.
-The difference in performance lies in our pragmatic BPMN encoding optimized for analysis and its direct implementation in an efficient programming language rather than using general model-checking tools.
-
-\textbf{Tool capabilities:}
-Another way to compare the different BPMN formalizations and analysis tools is to investigate their capabilities.
-Most tools formalize large parts of the BPMN specification and allow soundness and safeness checking~\cite{krauterHigherorderTransformationApproach2024,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022}.
-Some tools investigate additional aspects, such as the introduction of \textit{data} and \textit{time} during verification~\cite{houhouFirstOrderLogicVerification2022,corradiniFormalisingAnimatingMultiple2022}.
-Furthermore, other tools allow specifying and checking \textit{custom temporal logic properties}~\cite{krauterHigherorderTransformationApproach2024,corradiniFormalApproachAnalysis2021} and even provide graphical interfaces to ease the specification~\cite{krauterHigherorderTransformationApproach2024}.
-Moreover, some tools provide interactive BPMN simulation using token-flow animation~\cite{corradiniFormalisingAnimatingMultiple2022}, while others \textit{visualize counterexamples} for soundness violations using tokens~\cite{houhouFirstOrderLogicVerification2022}.
-
-Our tool focuses on \textit{instantaneous} control flow analysis and does not support custom properties, data, or time.
-We do not provide BPMN simulation since other tools already offer this.
-However, we use token-flow animation to visualize control flow errors interactively.
-This improves comprehension compared to previous static, less interactive visualizations.
-In addition, to the best of our knowledge, our tool is the only one that provides \textit{quick fixes}, i.e., automatic resolutions if control flow errors are detected.
-To sum up, our tool incorporates and enhances several ideas from the state of the art while adding novel concepts, such as quick fixes.
-We advocate for a pragmatic approach, prioritizing performance and understanding above all else to ensure seamless integration into BPMN modeling tools.
-
 \section{Conclusion \& Future Work} \label{sec:conclusion}

### 2024-08-01 paper.tex
Optimize space

@@
 In this paper, we describe a new tool, the \textit{BPMN Analyzer 2.0}\footnote{
-In the following, we will use BPMN Analyzer to refer to the BPMN Analyzer 2.0, not our previous work in~\cite{krauterHigherorderTransformationApproach2024}.}, for analyzing BPMN process models to detect control flow errors \textit{already} during modeling.
+In the following, we will use BPMN Analyzer to refer to the BPMN Analyzer 2.0.}, for analyzing BPMN process models to detect control flow errors \textit{already} during modeling.
 \autoref{fig:overview} shows an overview of the tool.
@@
 \textbf{Second}, we use \textit{tokens} to visualize errors \textit{interactively}, i.e., show an execution leading to the error.
-Our analysis provides sample executions leading to the possible control-flow errors, which we visualize directly in the BPMN editor by showing how tokens move from the process start to an erroneous state.
-We are unaware of other tools that visualize errors directly in the editor and allow for interactions, such as stopping/resuming, restarting, and speeding up the execution.
+Our analysis provides sample executions resulting in the found control-flow errors, which we visualize directly in the BPMN editor by showing how tokens move from the process start to an erroneous state.
+We are unaware of other tools that visualize errors in the editor and allow for interactions, such as stopping/resuming and restarting.
 
@@
 The quick fixes we support are described in detail in~\cite{krauterInstantaneousComprehensibleFixable2024} and can be extended independently of the formal analysis.
-We are unaware of other tools that offer fixes for identified control-flow errors.
+We are unaware of other tools that can fix identified control-flow errors.
 

### 2024-08-01 paper.tex
Shrink to 5 pages

@@
 \autoref{fig:overview} shows an overview of the tool.
-The tool front-end is based on the popular \textit{bpmn.io} ecosystem, while the analysis is implemented in Rust for performance and memory efficiency reasons.
-We implemented a breadth-first state space exploration.
-While generating the state space, we check BPMN soundness and safeness~\cite{corradiniClassificationBPMNCollaborations2018} \textit{on the fly} to uncover control flow errors.
+The UI is based on the popular \textit{bpmn.io} ecosystem, while the analysis is implemented in \textit{Rust} for optimal performance and memory efficiency.
+We perform a breadth-first state space exploration during which we check soundness and safeness~\cite{corradiniClassificationBPMNCollaborations2018} \textit{on the fly} to uncover control flow errors.
 Consequently, the tool can detect deadlocks, livelocks, starvation, dead activities, and lack of synchronization in BPMN models.
@@
 The BPMN Analyzer spends from 1 ms up to 9 ms for the BPMN models~\cite{krauterInstantaneousComprehensibleFixable2024} compared to 0.7 s up to 14 s in our previous tool~\cite{krauterHigherorderTransformationApproach2024}.
-In summary, the linear growth of the models leads to a linear growth in state space and, consequently, a linear growth in runtime.
+In summary, the runtime grows linearly with the state space.
 
@@
 This represents a \textit{worst-case} scenario for formal analysis.
-We generated a data set of models~\cite{krauterInstantaneousComprehensibleFixable2024} with a growing number of parallel branches with increasing length, as shown in \autoref{fig:parallel-branches-models}, like~\cite{corradiniFormalApproachAnalysis2021}.
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=0.5\linewidth]{images/parallel-branches}
-	\caption{Models with a growing number of parallel branches and branch length}
-	\label{fig:parallel-branches-models}
-\end{figure}
-
+We generated a data set of models~\cite{krauterInstantaneousComprehensibleFixable2024} with a growing number of parallel branches with increasing length, like~\cite{corradiniFormalApproachAnalysis2021}.
 \autoref{tab:parallel-branches-benchmark} shows the average runtime of our tool when analyzing these models.
@@
 \begin{table}[ht]
-% \scalebox{0.8}{ % TODO: Not sure about scalebox yet.
+\scalebox{0.9}{ % Resize to 90%
     \begin{minipage}{.51\linewidth}
@@
 	   \end{tblr}
-    \end{minipage}%
+    \end{minipage}
+    % Add extra space in the middle
+    \qquad
+    \qquad
     \begin{minipage}{.5\linewidth}
@@
     \end{minipage} 
-% }
+}
 \end{table}
@@
 The BPMN Analyzer takes 1-10ms for e001, e002, and e020~\cite{krauterInstantaneousComprehensibleFixable2024}, while~\cite{houhouFirstOrderLogicVerification2022} and~\cite{krauterHigherorderTransformationApproach2024} report 3.66-10.26s and 1-1.75s respectively.
-The benchmarks in~\cite{krauterHigherorderTransformationApproach2024} were run on the same hardware, while the machine used in~\cite{houhouFirstOrderLogicVerification2022} was slightly less powerful.
-To summarize, our analysis is instantaneous for nearly all models since most models have relatively small state spaces (less than 1000 states, see~\cite{fahlandAnalysisDemandInstantaneous2011}).
+The benchmarks in~\cite{krauterHigherorderTransformationApproach2024} were run on the same hardware, while the machine used in~\cite{houhouFirstOrderLogicVerification2022} was less powerful.
+In general, our analysis is instantaneous for nearly all models since most have less than 1000 states according to~\cite{fahlandAnalysisDemandInstantaneous2011}.
 
@@
 % Highlighting
-\textbf{First}, we highlight the problematic elements that cause control flow errors by directly attaching red overlays to them in the BPMN model.
+\textbf{First}, we highlight the problematic elements that cause control flow errors by directly attaching red overlays to them in the model.
 In addition, there is a summary panel in the top-right stating if any errors are found.
@@
 \textbf{Second}, we use \textit{tokens} to visualize errors \textit{interactively}, i.e., show an execution leading to the error.
-Our analysis provides sample executions resulting in the found control-flow errors, which we visualize directly in the BPMN editor by showing how tokens move from the process start to an erroneous state.
-We are unaware of other tools that visualize errors in the editor and allow for interactions, such as stopping/resuming and restarting.
+Our analysis provides sample executions resulting in the found control-flow errors, which we visualize in the editor by showing how tokens move from the process start to an erroneous state.
+We are unaware of other tools that visualize errors directly and allow for interactions, such as stopping/resuming and restarting.
 
@@
 The gateway \textsf{e1} will execute when resumed, resulting in two tokens at the subsequent sequence flow, i.e., an unsafe execution state.
-In addition, one can control the visualization speed using the bottom buttons next to the speedometer.
+Furthermore, one can control the visualization speed using the bottom buttons next to the speedometer.
 
 \subsection{Fixable Analysis}
-In addition to detecting, highlighting, and visualizing control flow errors, the BPMN Analyzer suggests fixes like \textit{quick fixes} in Integrated Development Environments.
+Besides detecting, highlighting, and visualizing control flow errors, the BPMN Analyzer suggests fixes like \textit{quick fixes} in IDEs.
 Quick fixes cannot be provided for all errors, but we currently cover many patterns leading to deadlocks, lack of synchronization, message starvation, and reused end events.
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{images/tool-screenshots}
+	\includegraphics[width=1\linewidth]{images/tool-screenshots}
 	\caption{Execution visualization (left) and suggested \textit{quick fixes} (right) in the BPMN Analyzer}
@@
 \section{Maturity of the Tool} \label{sec:maturity}
-The BPMN Analyzer is our newest tool, incorporating many findings from our previous work~\cite{krauterHigherorderTransformationApproach2024} while focusing on instantaneous and understandable error detectionn, as described in the previous section.
-The tool is open source~\cite{krauterInstantaneousComprehensibleFixable2024}, and we aimed to achieve high code quality by employing industry best practices such as rigorous static analysis, testing, and consistent formatting.
-Furthermore, we demonstrated the tool to companies in the BPMN process orchestration space and received positive feedback~\cite{krauterInstantaneousComprehensibleFixable2024}.
+The BPMN Analyzer is incorporates many findings from our previous work~\cite{krauterHigherorderTransformationApproach2024} while focusing on instantaneous and understandable error detection, as described in the previous section.
+The tool is open source~\cite{krauterInstantaneousComprehensibleFixable2024}, and we ensure high code quality by employing industry best practices such as rigorous static analysis and testing.
+Furthermore, we received positive feedback from companies in the BPMN process orchestration space~\cite{krauterInstantaneousComprehensibleFixable2024}.
 
-\section{Conclusion \& Future Work} \label{sec:conclusion}
+\section{Conclusion} \label{sec:conclusion}
 
@@
 
-In future work, we aim to improve our tool by providing more quick fixes, considering advanced BPMN elements such as different events, and ranking quick fixes based on usefulness and previous user behavior.
-Finally, we aspire to test our tool in a real-world scenario to gather feedback and measure its impact on productivity.
-
 \bibliography{bib}

### 2024-08-01 paper.tex
Final adjustments

@@
 \documentclass[
-onecolumn, % TODO: has to be one col
-% hf, % <-- Not sure if this should be enabled
+onecolumn,
 ]{ceurart}
@@
 
-% This was used to mitigate some warnings
-\usepackage[T1]{fontenc}
-\usepackage{lmodern}
 % Modern tables + extra stuff workaround
@@
 Consequently, the tool can detect deadlocks, livelocks, starvation, dead activities, and lack of synchronization in BPMN models.
-The BPMN Analyzer is open source and accessible online\footnote{\url{https://timkraeuter.com/bpmn-analyzer-js/}} alongside a video demonstration\footnote{\url{https://www.youtube.com/watch?v=Nv2W-hXNZYA}}~\cite{krauterInstantaneousComprehensibleFixable2024}.
+The BPMN Analyzer is open source and accessible online alongside a video demonstration\footnote{Tool: \url{https://timkraeuter.com/bpmn-analyzer-js/}, Video: \url{https://www.youtube.com/watch?v=Nv2W-hXNZYA}}~\cite{krauterInstantaneousComprehensibleFixable2024}.
 
@@
 	\centering
-	\includegraphics[width=0.5\linewidth]{images/overview}
+	\includegraphics[width=0.6\linewidth]{images/overview}
 	\caption{Overview of the BPMN Analyzer 2.0}
@@
 We generated a data set of models~\cite{krauterInstantaneousComprehensibleFixable2024} with a growing number of parallel branches with increasing length, like~\cite{corradiniFormalApproachAnalysis2021}.
+
 \autoref{tab:parallel-branches-benchmark} shows the average runtime of our tool when analyzing these models.
@@
 \begin{table}[ht]
-\scalebox{0.9}{ % Resize to 90%
-    \begin{minipage}{.51\linewidth}
+\scalebox{1}{ % Somehow needed
+    \begin{minipage}{.5\linewidth}
 	   \centering
@@
     % Add extra space in the middle
-    \qquad
-    \qquad
     \begin{minipage}{.5\linewidth}
@@
 
-\section{Conclusion} \label{sec:conclusion}
+\section{Conclusion \& Future Work} \label{sec:conclusion}
 
@@
 
+In future work, we aim to improve our tool by providing more quick fixes, considering advanced BPMN elements such as different events, and ranking quick fixes based on usefulness and previous user behavior.
+Finally, we aspire to test our tool in a real-world scenario to gather feedback and measure its impact on productivity.
+
 \bibliography{bib}

### 2024-08-01 paper.tex
Cleanup and typos

@@
-%% hf: enable header and footer.
-\documentclass[
-onecolumn,
-]{ceurart}
-
-% One can fix some overfills
-% \sloppy
+\documentclass[onecolumn]{ceurart}
 
@@
 
-% Rights management information. CC-BY is the default license.
+% Rights management information.
 \copyrightyear{2024}
@@
 \author[1]{Patrick Stünkel}
-[email=past@hvl.no] % patrick.stuenkel@hvl.no
+[email=past@hvl.no]
 \author[1]{Adrian Rutle}
@@
 The UI is based on the popular \textit{bpmn.io} ecosystem, while the analysis is implemented in \textit{Rust} for optimal performance and memory efficiency.
-We perform a breadth-first state space exploration during which we check soundness and safeness~\cite{corradiniClassificationBPMNCollaborations2018} \textit{on the fly} to uncover control flow errors.
+We perform a breadth-first state space exploration to check soundness and safeness~\cite{corradiniClassificationBPMNCollaborations2018} \textit{on the fly} to uncover control flow errors.
 Consequently, the tool can detect deadlocks, livelocks, starvation, dead activities, and lack of synchronization in BPMN models.
@@
 Developers of industrial BPMN software also like our tool, especially the End-to-end user journey~\cite{krauterInstantaneousComprehensibleFixable2024}.
-Thus, this supports our claim that the UI is easy for users unfamiliar with formal analysis to understand.
+Thus, this supports our claim that the UI is understandable for users unfamiliar with formal analysis.
 
@@
 
-% Must have section according to the description
-% A section discussing the innovations of the tool or resource to the BPM community and its main characteristics or features
 \section{Innovations} \label{sec:innovations} % Main tool description and showing the innovations
@@
     \end{minipage}
-    % Add extra space in the middle
     \begin{minipage}{.5\linewidth}
@@
 \section{Maturity of the Tool} \label{sec:maturity}
-The BPMN Analyzer is incorporates many findings from our previous work~\cite{krauterHigherorderTransformationApproach2024} while focusing on instantaneous and understandable error detection, as described in the previous section.
+The BPMN Analyzer incorporates many findings from our previous work~\cite{krauterHigherorderTransformationApproach2024} while focusing on instantaneous and understandable error detection, as described in the previous section.
 The tool is open source~\cite{krauterInstantaneousComprehensibleFixable2024}, and we ensure high code quality by employing industry best practices such as rigorous static analysis and testing.

### 2024-08-01 paper.tex
Minor fixes

@@
 The benchmarks in~\cite{krauterHigherorderTransformationApproach2024} were run on the same hardware, while the machine used in~\cite{houhouFirstOrderLogicVerification2022} was less powerful.
-In general, our analysis is instantaneous for nearly all models since most have less than 1000 states according to~\cite{fahlandAnalysisDemandInstantaneous2011}.
+Our analysis is instantaneous for nearly all BPMN models since most have less than 1000 states, according to~\cite{fahlandAnalysisDemandInstantaneous2011}.
 
@@
 Our analysis provides sample executions resulting in the found control-flow errors, which we visualize in the editor by showing how tokens move from the process start to an erroneous state.
-We are unaware of other tools that visualize errors directly and allow for interactions, such as stopping/resuming and restarting.
+We are unaware of other tools that visualize errors directly and allow interactions, such as stopping/resuming and restarting.
 
